\documentclass[char]{guardians}
\begin{document}

\name{\cAmaterasu{}}

You are Amaterasu who shines in the heaven, the goddess of the sun and the universe, the daughter of Izanagi, the sister to Susanoo and Tsukuyomi. You also find yourself to be the very last of the kami. Although you intend to continue watching over the Earth and its scattered peoples for as long as you can, you admit to yourself that it is lonely with your family having long since dispersed among the stars.

Long ago, you and your siblings walked with the Japanese people throughout their long history. Your people suffered when your family had its rivalries and prospered through your fleeting moments of joy. But that was all in the distant past. At some point, you and your family were pulled through a powerful vortex by an entity called the \cWarden{}. Ever since then you have been living in a bubble, disconnected from the Earth but still able to watch humanity's troubles. There are other gods in the bubble with you from other places, most of whom perceive this to be a grand prison they must fight tooth and nail to escape from. You feel differently --- human-made troubles like pollution or deforestation are nothing compared to the damage that could be caused by the likes of Odin or Zeus being unleashed on the Earth. Since the greatest dangers to humanity reside in this strange bubble with you, your charge is to remain here as well to watch over the other gods.

Time moves differently for the kami, but it still moves. When you first arrived, a being called the \cCaretaker{} welcomed your whole family to the Celestial Containment Complex and moved you into a facsimile of Takama-ga-hara, the plain of high heaven. Here you have resided, while the gods from other pantheons resided in realms modeled after their ancestral homes. Like the Greeks and the Norse, your family did not take well to its captivity at first, but over the centuries things settled down. But one day, your brother Susanoo felt the call to move beyond this world to the next one. The \cCaretaker{} and \cWarden{} escorted him to a great ship that carried him into the stars. Over the intervening years, the rest of your family slowly felt the call and eventually they too were all similarly escorted away. Gods from other pantheons also felt the desire to travel the stars, although many resisted their lure with little success. Still, things changed a thousand years ago when the \cCaretaker{} and \cWarden{} lost contact with the Guardians. Ever since contact was lost, no great ships have arrived to carry gods into the stars and the \cWarden{} will not permit any gods to leave without such an escort. This problem reached its peak when Thor and Set felt the call. Eventually, Set was angered at his continued captivity to the point where he exploded in a violent burst of energy felt throughout the realms, and Thor mysteriously vanished.

Normally, you spend your time within Takama in solitude. Occasionally, you have visits from the \cCaretaker{} or \cWarden{} who have granted you a viewing portal from which you can watch events on Earth unfold. You also have occasional visits from a strange young man called \cJascha{\intro}. You are not really sure what his role in the Complex is, as he appears to be in every way human but hasn't aged in a thousand years. Unlike all the other residents, \cJascha{} is able to move freely between the realms of the gods. You suspect he was involved in this prison's creation, but he does not seem to be able to remember any details from his past.

Every one hundred years, the \cCaretaker{} brings all the gods to the central courtyard for what \cCaretaker{\they} refers to as a team-building exercise called the \pGames{}. You find the other gods to provide a very different perspective but they are also fickle, capricious, and take actions with absolutely no regard for the consequences. While you are content to be left to your contemplations in Takama, the other gods appear to thirst for each other's blood and need to prove their superiority over each other like adolescent boys. Although the Shinto pantheon used to participate as well, this stopped once you became the only remaining member. Instead, the Greek and Norse pantheons petitioned you to take over the \cCaretaker{}'s role as the arbiter of the games. You find the games to be an odd contrivance, but you silently enjoy your role as a judge and believe you do quite a good job at it, even though it feels like managing a horde of rowdy children.

Things have been fairly repetitive these past 500 years, but today things changed abruptly. The \cCaretaker{} summoned everyone to the courtyard to announce the imminent arrival of \cUnity{}, a new kami from the modern age. The \cCaretaker{} placed you in charge of organizing an impromptu version of the Games to welcome \cUnity{} to \cUnity{\their} new home. The \cCaretaker{} and \cWarden{} then took the \stone{} and left to prepare for Unity's arrival. This round, the gods seem quite intent on taking the Games seriously and have wagered three items of immense power on the outcome of the games. The \cCaretaker{} has secured these items and will release them when you announce the winning pantheons at the conclusion of the Games in three hours.

The other gods reside under the delusion that the \cCaretaker{} and \cWarden{} are members of a rival pantheon, out to punish and control them, and they cannot accept the implications of a star-spanning race like the Guardians. But you are the goddess of the universe, and your perspective is vast. You understand that the Guardians are a race with strengths and flaws not unlike humans. But you also know that there are other races that fight against the Guardians, and you have always felt that somewhere within this Complex there rests such a being. You do not know its form, only that it is a clever Tengu and it has been lurking here a very long time. Whatever form this dark spirit takes, it easily masks its presence from the \cWarden{} and \cCaretaker{}. From its aura you are certain that its hunger for souls is insatiable and that it holds all the gods here in the greatest contempt. Although the \cWarden{} has always ignored your warnings, you have felt the spirit begin to stir with the recent arrival of \cUnity{}, as if it senses an opportunity to escape. You are the only one here who seems to sense this danger and will not let this spirit break free from its prison at any cost.

You have lots of concerns for the Earth. At the forefront is allowing this dark spirit to escape, followed closely by the escape of some of the more dangerous gods like Zeus, Odin or Anubis. But in the longer term, you fear that the human population is asking the Earth to change faster than it can adapt. To alleviate this problem, you have been spending your time in Takama designing a powerful artifact you call the \iSeed{\MYname}. The purpose of the Seed is to make subtle changes to the Earth's biomes to better handle the pressures placed on them by modern humans. It won't allow the planet to instantly absorb ever-growing amounts of pollution, but it will protect some of the most fragile ecosystems. The Seed is not yet completed, but you are almost done --- you just have to leverage a bit of power from the other gods. But by itself the Seed is of no use unless you can get it outside the Complex and planted on the Earth. Previously you had no idea how to accomplish this, but Unity's arrival gives you some hope. You are willing to leave yourself, but planting the Seed is very simple and it would be just as simple to convince someone else to deliver the Seed for you. Still, it is a powerful artifact you have invested considerable energy in and it would be dangerous if it fell into malicious hands.

The \cWarden{}'s methods are overly severe, but \cWarden{\they} is not wrong --- the gods are dangerous and must be contained. You are fine with them returning to the stars like your family, but for the vast majority of gods you would rather kill them yourself than let them terrorize the fragile human population. In the past, escape has never been an option so you have never needed to bring up these thoughts to the \cWarden{}, but Unity's arrival has changed things. You have not judged \cUnity{} yet, but you did have a brief conversation with the newly arrived human, \cKachiko{}. \cKachiko{\They} seems quite lost and confused but \cKachiko{\they} has a strong spirit and it amuses you to think that like the Emperor of Japan, \cKachiko{\they} might be one of your descendants.

\begin{itemz}[Goals]
  \item Protect the Earth and prevent any gods you deem overly dangerous from escaping.
	\item Hunt down and slay the dark spirit that has been lurking within the Complex. Prevent it from escaping at any cost.
	\item Complete the Revitalization Seed and get it planted on the Earth, either by yourself or someone you trust.
	\item Fufill your role as arbiter of the \pGames{}.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} An ancient dragon who called this council meeting.
\end{contacts}

\end{document}
