\documentclass[char]{guardians}
\begin{document}
\name{\cAthena{}}

You are an ethereal -- a space faring spirit that thousands of years ago reached earth along with the rest of your swarm. You imprinted on the idea of \cAthena{}, while many of your kin imprinted on other Greek Gods. In some ways you \emph{are} \cAthena{}, Greek goddess of war and wisdom, daughter of \cZeus{}, advisor to Odysseus, patron goddess of Athens; in other ways, you are just a little lost soul, trapped, alone, and very far from home.

When you and your family first arrived on Earth, you had dominion over it all. During that time you were all convinced you were truly Greek Gods. After only a couple of hundred years of this however, you were all corralled by two beings, the \cCaretaker{} and the \cWarden{}, in something called ``The Complex'' along with the Norse, Egyptian and Shinto pantheons. Apparently the Greeks weren't the only civilizations with belief powerful enough to give life to their gods.

Initially, all of the gods were kept together, in the same sparse prison. But things quickly deteriorated once it was clear that the other Pantheons would not bow their proud backs to the superior Greek gods. To mitigate the fighting, the \cCaretaker{} and \cWarden{} used something called the \stone{} to create crude replicas of each Pantheon's home realm and locked each Pantheon in their own. \cZeus{} quickly realized that with the power of the \stone{}, the Greek Pantheon could build their \emph{own} Mt. Olympus, beyond the reach of the \cCaretaker{} and the \cWarden{}. It has been his driving goal for over 1000 years. As a loyal member of the Pantheon, you support the endeavor, although your brother \cHephaestus{} has been point on the project. When called upon to act, you will do so.

In close quarters, the Greek gods were little better than all of the pantheons together. The infighting was nearly unbearable until the \cCaretaker{} had another ``brilliant'' idea. \cCaretaker{\They} decided that some ``team building'' exercises would be great for reducing tension in The Complex. So were born the \pGames{}. Every hundred years or so, each pantheon would wager an item of middling power, and compete in a series of contests to prove superiority. Of course the Greeks dominated the competition -- until your numbers started to dwindle.

It took you about 300 years to come to terms with the idea that you weren't a God, but being the goddess of wisdom meant that you could put all the pieces together much better than the other gods. You wanted very much to believe you were a god, but the logic of the \cCaretaker{} was flawless. Still, it didn't seem to matter what species you were. The humans saw you as \cAthena{}, and thus you were \cAthena{}. The rest of your family did not accept the logical conclusion though, and continued to live in denial. How their denial survived what happened next is beyond your comprehension. 

One by one, your family began to feel \emph{the call}. They would slowly grow less interested in watching earth, less hungry to escape the control of the \cWarden{}, and become more and more absorbed in staring at the stars. They started to speak dreamily of a vague place, far away that they missed. They wanted to go ``home'' to a place you had never seen. Whenever this happened, the \cCaretaker{} would call a big celebration, and then \cCaretaker{\they} and the \cWarden{} would escort your aunt, uncle, or sibling away, to a big ship belonging to a species called ``the guardians''. You never saw them again.  According to the \cCaretaker{} the celestial was entering it's next life-phase and was returning to the spawning grounds. It all sounded very far fetched to you, but if the facts fit\ldots{}

Recently you have begun to long for the stars, but there has been no party, and no great ship to carry you home. The \cCaretaker{} and \cWarden{} are very agitated about this. It probably has something to do with Set and Thor. About 500 years ago, they too felt the call, but no ship came to take them away. As madness started to creep into Set's eye, the \cCaretaker{} and \cWarden{} came almost to blows. You had never seen the two of them disagree about something before.  Eventually, an unexplained explosion rocked The Complex. Neither Set nor Thor was heard from again. This mystery you have never been able to explain. It is impossible to kill a God, and yet, it would seem that Set and Thor had been killed by the explosion. The cheerful mood of the usually dour \cWarden{} in the months following the incident left you very suspicious. You are beginning to fear for your own life.

To take your mind off of the stars, at least for a little while, you have started spending time with \cFenrir{} and \cVal{}. Well, as much time as is possible, given that the pantheons are still kept in separate cells except during the \pGames{}, even as your numbers dwindle to just a handful. In the mean time, you send messages back and forth through \cJascha{}, a human who is more than he appears. He is old, so very old, and smart, so very smart -- even with his failing memory -- and the \cWarden{} and \cCaretaker{} show him great deference and allow him to wander between the realms when no one else is allowed to do so.  Despite this limitation, you and \cFenrir{} and \cVal{} have become somewhat of friends. \cVal{} is a warrior, and shares your love of weapons. Together with your \cHephaestus{\sibling}, \cHephaestus{} you two are concocting plans for a powerful new weapon. \cFenrir{} is a newer contact. You had never been sure how exactly to interact with \cFenrir{\them}, as \cFenrir{\they} is a wolf, but it turns out that \cFenrir{\they} is really smart. \cFenrir{} had come to a similar conclusion about what happened to Set and Thor, and has sympathy for your plight. \cFenrir{} has revealed to you that \cFenrir{\they} too is feeling the call of the stars. The two of you are working desperately to find a way to contact the Guardians, the people who are supposed to send the ships to escort you away. \cFenrir{}'s technological skills are astonishing, and have proved invaluable in your quest.

This association of yours with the Norse drives your \cHera{\parent}, \cHera{} to distraction. \cHera{\They} loves to yell at you about compromising the pantheon, cavorting with the enemy, yadda yadda yadda. \cHera{\They} is really controlling, and wants to dictate your every waking moment one day, and expects you to read her mind the next. You are convinced that captivity is wearing on her sanity. Just yesterday for example, \cHera{} came to you and asked if you would ever consider subverting \cZeus{}'s plans to be acceptable. You just don't \emph{do} that. Your \cZeus{\parent} is the leader of the Greek pantheon. What could \cHera{} be thinking? You told her as much, and she totally over reacted.  After a 40 minute row, in which \cHera{} criticized everything about you from your new friends to your desire to leave for the stars, you slammed the door in \cHera{\them} face. You aren't speaking to your \cHera{\parent} until she apologizes.

The arrival of \cUnity{} and \cKachiko{} has certainly stirred things up in the Complex. The next couple of hours is going to be very interesting.

%%Anubis plus scales

\begin{itemz}[Goals]
  \item Win the \pGames{} to prove Greek superiority.
  \item Help \cZeus{} use the \stone{} to create a new Mt. Olympus.
  \item Build a communication device to call the guardians to summon a ship.
  \item Work with \cHephaestus{} and \cVal{} to build a new kind of weapon.
  \item Make \cHera{} apologize.
\end{itemz}


\begin{contacts}
  \contact{\cZeus{}} Your \cZeus{\parent} and the leader of the Greek Pantheon.
  \contact{\cHera{}} Your \cHera{\parent}. The two of you are having a fight right now.
  \contact{\cPandora{}} Your human \cPandora{\sibling}.
  \contact{\cHephaestus{}} Your \cHephaestus{\sibling} who is also super excited about building the bomb.
  \contact{\cVal{}} A friend of yours helping you build the bomb.
  \contact{\cFenrir{}} A friend of yours helping you build the communicator.
\end{contacts}

\end{document}
