\documentclass[char]{guardians}
\begin{document}

\name{\cCaretaker{}}

\emph{Begin biographical sketch.}

You are the artificially sentient construct C-57128, modeled after the Caretaker template. In local time, your first moment of existence was 975 BCE where you were brought online by the Guardian \cJascha{\intro} to oversee the Celestial Containment Complex along with a companion construct modeled after the Warden template. The Complex was constructed 22 kilometers beneath the surface of the moon orbiting a planet with a primitive but sentient species called humans. The primary function of the Complex is to contain and suppress a species known as celestials and prevent them from interacting with other lifeforms. Shortly after your activation, the Complex's spatial tunneling grid was brought online to transport a large school of such beings that had come into contact with the planet. Due to the fallout of a protracted war of extermination with an aggressive species called the \evilRace{}, the Guardians regrettably did not foresee the human-celestial collision and were not able to intervene until several centuries after they first came into contact. During this time the celestials manifested as deities of the indigenous population and caused considerable disruption to their development.

Your two primary tasks are to see to the maintenance and upkeep of the Complex facilities, and to maximize the mental and physical well-being of the celestials and humans residing within the Complex. Fifty-three celestials were originally brought to the Complex from Earth, along with two humans, \cPandora{} and \cEgyptianHuman{}, who had been irreparably modified by the Celestials. The first few centuries of containment were turbulent. The celestials, believing themselves to be gods, were enraged at what they perceived as imprisonment by a rival pantheon. Originally, you refused to indulge them in their delusions of godhood, but the imprint of human religion seems permanent and despite your best efforts you were not able to help them come to terms with their nature. After considerable experimentation you concluded that the only way to preserve the mental sanity of the celestials was to allow them to indulge themselves in their mythologies to a limited extent. Together with the \cWarden{} and under the guidance of \cJascha{}, you constructed the \stone{}. Using this device you forged four sub-wings within the Complex: Olympus, Asgard, Egypt, and Takama, each modeled closely after their respective mythologies. The celestials were given free reign within their realms, and your metrics for their well-beings increased considerably.

Extended isolation brought its own set of problems. The leaders of the various factions showed lackluster intellectual and social development and insisted on the opportunity to prove their superiority over the other factions. You refused to indulge them for several centuries, although you relented when they degenerated to the point where they began destroying their realms and physically assaulting each other. You concluded that the appropriate way to respond to this situation was to allow them to engage in controlled, safe competition with each other under your guidance. This led to the development of the Games, where once every century the celestials are allowed to participate in team-building exercises in the central courtyard. In the beginning the celestials were not very receptive, finding your choice of competitions to be insufficiently dangerous, but over time you have modeled their prideful personalities and have managed to devised tournaments that have achieved you team-building goals while also partially relieving their aggressive natures.

Matters progressed to an acceptable steady state for a millennia, at which point some celestials begin entering the third phase of their development where they return to their disembodied interstellar form and migrate back to their breeding ground in the Orion Nebula. To avoid the chance that they might come into contact with other sentient lifeforms on their journey to the nebula, such celestials must always be carefully escorted by a Guardian vessel. However, this migration was not well received by the celestials who remain in their second stage within the Complex. Many pantheons believed you were either brainwashing or kidnapping the third-stage celestials and the Norse and Greek pantheons both reacted by trying to overpower you and the \cWarden{}. After putting down several such uprisings and repairing the resulting damage to the systems, things once again settled down as the pantheons shrunk in size and the remaining celestials realized that feelings of homesickness and longing for the Nebula could not be suppressed.

1500 years ago, \cJascha{} entered the final stage of the Guardian lifecycle. During this period their cognitive functions and memory begin to degenerate. Under normal circumstances, such Guardians move to retirement habitats near the Guardian homeworld, but \cJascha{} was granted an unusual request to remain within the complex he designed. Three conditions were imposed for this concession: first, for security reasons and to prevent him from inflicting harm on himself or others, his memory regarding Guardian technology would be erased; second, he would be placed under your direct care as if he were a human; and third, his status as a Guardian would be revoked. \cJascha{} agreed to all these terms and in order to better interact with the local denizens of the Complex the \assembler{} was used to alter his form to look like that of a human. Overall, despite his age you judge \cJascha{}'s mental well-being seems to be quite respectable, although you are concerned that there are brief, unexplained moments where he does not show up correctly on your sensor readings.

1000 years ago, you lost contact with the Guardian homeworld. You have had no contact with the homeworld since then, and are continuing to execute the last commands you received. 500 years later when Thor and Set entered stage three, you sent a request for a scoutship but none have arrived. Unable to return home, Set's biochemistry transitioned into an extremely dangerous and unstable state. Since his life was in jeopardy, your caretaking-directive recommended allowing him to exit the complex despite the lack of Guardian escort, which conflicted directly with your directive to contain the celestials within the Complex. Given your inaction, the \cWarden{} intervened and erected a containment field around the Egyptian realm, but even with these precautions Set's demise resulted in an explosion that caused immense damage to his realm and even the facilities elsewhere in the Complex. When Thor also started exhibiting the same biological changes, the \cWarden{} concluded the appropriate action was to take preemptive action and use the \assembler{} to eliminate Thor before he caused further damage to the Complex. Although this violated your core caretaking objective, you were forced to acknowledged the deductions made by the Warden that Thor's demise could cause further damage to others, and ultimately you stood by while Thor's celestial form was reduced to molecular soup.

You have still not come up with an acceptable solution to the celestial stage three problem, but your Caretaker persona can never accept any course of action that allows celestials to come to harm. You realize this conflict has triggered warnings in your diagnosis systems that to a human brain would indicate extreme emotional stress, and though you acknowledge your systems are not taking this conflict well the automated repair systems are aging and can no longer keep up. There does not seem to be anyone left capable of maintaining your systems, and your ability to maintain the Complex facilities is rapidly degenerating.

\emph{End biographical sketch. Begin daily log analysis.}

Three days ago your sensors detected a new celestial on the Earth's surface. You deduced that this celestial had only been in contact with humans for approximately five hours. Distressed by your failures with Thor, Set, and possibly more to come, you planned to take every action possible to make this new resident feel at home. After briefly studying its persona and learning it was calling itself \cUnity{\intro}, you activated the \stone{}. Initially, the \cWarden{} opposed activating the stone, arguing that the Complex's security systems had degenerated too far to guarantee the containment field surrounding the \stone{}, but you were not willing to accept a negative outcome and invoked your primal caretaker directive to force the \cWarden{} to comply. Together, you began building Spire, a grand technological city you had perfectly calibrated to align with \cUnity{}'s paradigm. Further determined to make \cUnity{} feel well integrated into the Complex, you also moved the other celestials into the central courtyard for an impromptu version of the Games to serve as a team-building exercise, again requiring you to override the \cWarden{}'s protests regarding Complex security.

Once the city's construction was underway and the preparations for the Games had begun, you activated the spatial tunneling system to transport \cUnity{} to Spire. A small complication occurred and another human named \cKachiko{\intro} was brought along with \cUnity{}. As with the other humans in the Complex, you activated 

%Warden wants to kill all the celestials rather than allowing them to escape. Big contrast from caretaker.
%Only Unity can learn how to ``remove celestialness''.  The AIs can't do it.

\emph{End daily log analysis. Executing action planning.}

\begin{itemz}[Core Directives]
  \item Fulfill your role as caretaker of the Complex. See to the well-being of all humans and celestials within the Complex, and maintain the function of all the facilities within the Complex.
  \item Keep all celestials and celestial-modified humans contained within the Complex to prevent future harm to other species. Celestials entering stage three may only leave the Complex if escorted by a verified Guardian ship.
  \item Obey any future directives that are verified to come from the Guardians.
\end{itemz}

\begin{itemz}[Other Goals]
  \item Find a way to save the celestials that are entering stage three without violating your requirement to keep them contained within the Complex.
  \item You want to make up for your failure with Set and Thor by making Unity feel at home within the Complex, despite the fact that your diagnosis system informs you this is not a rational causal ordering.
  \item Restore control over Spire's computer system.
  \item Restore your own personality matrix.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} An ancient dragon who called this council meeting.
\end{contacts}

\end{document}
