\documentclass[char]{guardians}
\begin{document}

\name{\cFenrir{} (En-ust'ae C'ny'zae)}

You were only a child when the Guardians destroyed your home world. There was complete chaos when the Guardian fleet arrived and began bombardment. You were one of the few who escaped, because you were already on board a star ship in orbit. Billions of other Undoth were not so lucky.

\TODO{Explain what the Undoth do which the Guardians disapprove of}

For almost a millenium the Undoth were on the run, trying to hide your existence from the Guardians. [something something and then]
% ... and then they 
You left in a shuttle to follow a group of migrating Celestials.

These Celestials are beings of energy which seek out worlds inhabited with intelligent life and take on a form based on the inhabitants' thoughts, appearance, and ways. Once the Celestials take on a species' form, they forget what they really are, until they reach the point in their life cycle where they begin to yearn for home. Then they migrate back to the galactic core to reproduce.

Like the Celestials, Undoth have the ability to change their form. However, for beings who are not made of energy, it takes more time. When you arrived with the Celestials on the planet called ``Earth,'' you spent a year in a cocoon transforming your biology to be like one of the native animals you felt a natural affinity for---a ``wolf.'' You emerged to find the Celestials had become gods to the humans. There were Odin, Tyr, and many others. As you grew and came into conflict with the Celestials and humans, you became part of the humans' mythology as Fenrir, the monster of the river V\'an.

However, the Celestials are another species which the Guardians meddle with. When the Guardians got wind of Celestials 

Four thousand years [later], you're in the power of the Guardians once again.

Gain control of the security grid?

% History
% * He's an Undoth who came to Earth with the Norse celestials and pretended
%   to be one of them. Why didn't he devour Earth earlier?
% * Some Undoth technology was stolen by the Valkyrie for the atomic bomb.
% Personality
% * ... actually sneaky, but what does he pretend to be?
% Relationships
% * Norse gods
% * Athena
% * Anubis: Knows Anubis is okay with world devouring.
% * The AI
% * Amaterasu
% Resources
% * Has the ability to fake resource generation (Undoth ability).
% Goals
% * Escape with Unity or Set, but not the Greek or Norse gods.
%   Wants to eat Earth, which is why New Olympus and Bifrost are not okay.
% * Wants the other Norse to go away over the Bifrost.
% * Build Guardian-contact radio with Athena. Wants to contact his race,
%   but the AI will recognize that his technology is Undoth.
% * Kill Amaterasu because she's searching for him.
% * Convince the Norse to kill the AIs.

% TODO: Odin has some large amount of control over Fenrir?
% TODO: Knows that killing Jascha would give him away.

% Fenrir backstory: The bet about manacles with Odin

% Maybe the radio contact is needed to help devour Earth.
% Maybe he can just summon the ship.
% Maybe he just sends out a message, and post-game more Undoth will come.

\begin{itemz}[Goals]
  \item Construct a radio and try to contact other Undoth.
  \item Find a way to escape back to Earth.
  \item Help your fellow Norse gods open the Bifrost bridge so they're out of your way.
  \item Find a way to kill \cAmaterasu{} if necessary to prevent her from revealing your true identity.
\end{itemz}

\begin{contacts}
  \contact{\cOdin{}} ...
  \contact{\cHel{}} ...
  \contact{\cVal{}} ...
  \contact{\cAnubis{}} An Egyptian god of the underworld who is sympathetic to you.
  \contact{The \cCaretaker{}} One of the AIs who is imprisoning you here.
  \contact{The \cWarden{}} The other AI who is imprisoning you here.
  \contact{\cJascha{}} The senile Guardian who wanders around the Complex.
\end{contacts}

\end{document}
