\documentclass[char]{guardians}
\begin{document}

\name{\cIsis{}}

\TODO{Cross reference with Osiris's sheet}

% Introduce info about what kind of god she is as needed.

% What was her relationship with Geb?
% She probably knew of Geb doing something Anubis would judge unjust.
% What might that be?

% Isis might think Osiris was responsible for Set's demise.

% Isis and Anubis know Osiris lost his powers.
% Doesn't know that Osiris is working with Hera to get them back.
% Has that conflict with Hera.

% Isis and Anubis are mad that Osiris put up the Necronomicon for the games.
% They think he's taking a stupid risk (and he thinks they're taking a stupid
% risk).

% Isis SHOULD NOT TRUST non-Egyptian gods besides maybe Hel.
% In particular, should be wary of trusting Unity.
% Maybe Geb's death is what make it hard for her.
% But escaping is still her first priority, and if Osiris forces her hand,
% she'll go with Unity as much as she dislikes him. She might also knock
% Osiris unconscious so they can drag him along when the escape with Set.

% Isis will backstab Set once she gets the info from him.
% Can't be too obvious about it though.

% Mempack if Geb's heart is judged unjust. (Not okay!)

% NOTE: There should be some preparation for escaping which is shared
% between the two methods of escaping.

% NOTE: More interaction with other pantheons?

% NOTE: Willing to knock Osiris unconscious and drag him along if that's
% the only way to resurrect Set and escape.

% NOTE: Knows that if Osiris gets the book back, she'll have to knock him
% out and take it from him to use it.

% NOTE: If Osiris gets his powers back, he can protect them from Set?

% TODO: Set was not actually trying to escape. What help can he provide?
% Increase the number of people who escape with Unity?
% Substitute the Egyptians for other people escaping with Unity?
% What if Osiris and Set both help?
% TODO: Set will not be yearning for the stars.
% TODO: Two ways to resurrect; necronomicon and pandora's box.





You well remember the day you were torn out of Egypt and brought to this horrible place.
% Maybe Geb was brought along with her. Others don't really know.
% She's protective of Geb.

In time, your jailers decided to hold a competition between the pantheons every hundred years. These Games brought you into contact with the gods of the other pantheons: Norse, Greek, and Shinto. These gods are strange and foreign to you. You enjoy the company of some of them, such as the Norse goddess \cHel{}. Others, like \cHera{}, you can't stand. She acts like you're encroaching on her role as goddess of marriage. Personally, you don't think she deserves that aspect, unless she's just claiming to be the goddess of wives who nag their cheating husbands.

% What else?

Five centuries ago, \cSet{} began to long for the stars. However, he died before the \cWarden{} and \cCaretaker{} could take him away. The cause of his death was an explosion that rocked the entire Complex and clearly worried even the \cWarden{} and \cCaretaker{}. You never found out what the cause of the explosion was, but you would not be surprised to find out that \cOsiris{} had something to do with it. \cAnubis{} suspected that \cSet{} was trying to circumvent your overseers' spells of protection in a desperate attempt to get out of the Complex, and unintentionally caused the explosion.

Eventually the three of you gods who remained, along with \cEgyptianHuman{}, decided to escape the Complex. Although the \cWarden{} and \cCaretaker{} have powers far beyond yours, they are not omnipotent, as they were clearly unsettled by the explosion which killed \cSet{}. At the most recent Games, you decided you could trust the Norse goddess \cHel{} enough to include her in your plans to escape.
% TODO: Why?

Since then you have discussed your plans using coded messages passed between pantheons by \cJascha{}, a mortal who your overseers have seen fit to allow free travel between all your realms. You've discussed many ideas, but only one has a real chance of working. If you can resurrect \cSet{}, he may have knowledge of how to  \cWarden{} and \cCaretaker{}. At the very least, having an ally your overseers don't know about is certain to help. \cOsiris{} has strong objections to this plan. You understand his loathing for \cSet{}, but escaping the Complex is too important to let that get in the way.

% TODO: Reconcile the above paragraph with the ways Set can actually help.
%       Maybe Set can help them escape by the same method Unity can, and
%       Set and Unity can also pool their powers together (but Osiris needs
%       to work with Unity; can't do it alone). Combined powers scale sub-
%       linearly? (E.g. if each can take 4 alone, together they can take less
%       than 8.)
% TODO: The whole ``four hour'' thing needs to be in here, and in osiris's
% sheet.
% TODO: Knows above that \iNecro is needed.

Two days ago a new god named \cUnity{} was brought to the Complex, for the first time in millenia. When the \cWarden{} and \cCaretaker{} announced the Games were going to be help immediately because of \cUnity{}'s arrival, \cOsiris{} immediately gave them the \iNecro{\MYname} as your pantheon's wager in order to delay any attempt to resurrect \cSet{}. You're beginning to be fed up with his resistance to your escape plan. At any rate, you'll need to win back the \iNecro{\MYname} in one of the competitions, or maybe you can find another way to resurrect \cSet{} without it.

Yesterday, you saw signs that the power of the \cWarden{} and the \cCaretaker{} has begun to weaken. For a few moments, parts of Egypt flickered in and out of existence, and then all was back to normal---except that \cEgyptianHuman{} killed by a falling pillar. \cEgyptianHuman{}'s death has broken your heart. You have now failed every single one of your worshippers. Neither of the others seems to care: \cOsiris{} is only angry that there is nobody to worship him, and \cAnubis{} just embalmed \cEgyptianHuman{}'s heart in preparation for judgement. You begged \cAnubis{} to have mercy and refrain from judging him:
% TODO

\begin{itemz}[Goals]
  \item Regain the \iNecro{} for your pantheon.
  \item Resurrect \cSet{}, either using the \iNecro{\MYname} or some other method.
  \item With \cSet{}'s help, escape the Complex with your pantheon and \cHel{}---even if it means knocking \cOsiris{} unconscious and dragging him with you over his objections.
  \item Don't allow \cAnubis{} to weigh \cEgyptianHuman{}'s heart against the \iFeather{\MYname}.
  \item Find out what caused the event that killed \cEgyptianHuman{}.
\end{itemz}

\begin{contacts}
  \contact{\cOsiris{}} Your husband. You love him dearly, but the issue of \cSet{} is beginning to drive a wedge between you.
  \contact{\cAnubis{}} The god of the afterlife, who judges the dead.
  \contact{\cHel{}} The Norse goddess who is in on your plans to escape.
  \contact{\cCaretaker{}} One of the beings who is imprisoning you here.
  \contact{\cWarden{}} The other being who is imprisoning you here.
\end{contacts}

\end{document}
