\documentclass[char]{guardians}
\begin{document}

\name{\cKachiko{}}

My name is \cKachiko{\intro}. I come from a middle-class Japanese family, have a degree from the top robotics program in the United States, and after graduating I returned to Tokyo to found Kachicorp which I built from the ground up into a small but rapidly rising robotics company. I have a personal hand in every product my company makes and I work constantly to fundamentally changing the way we interact with robots in our daily lives. This is how my morning schedule was supposed to go: 9:00am, coffee with my secretary to go over the company finance report; 9:30am preparation for the 10:00am meeting with the marketing team regarding the upcoming convention in Yokohama; lunch at noon; 1:00pm working in the lab with my engineering team. This is, not, in fact, how my day has gone. I am not certain I will be home in time to take the roast out the oven for dinner. I may or may not be alive by then.

At the end of my marketing meeting, a new event showed up on my schedule. My secretary informed me that my CTO had recently vetted an exceptionally talented new hire and that based on his excited tone it was absolutely imperative that I meet with the candidate in person if we were going to have a chance of hiring \cUnity{\them}. I made a mental note to remind my employees that we are a growing company and they will need to give me more than a few hours notice when these sorts of situations arise, but decided to just meet with the candidate over my lunch break. From the moment the candidate entered my office, I knew that \cUnity{\they} was like no one I had ever met before. \cUnity{\They} introduced himself as \cUnity{\intro}, and immediately jumped into a discussion so entrenched in technical detail that it was all I could do to keep up. \cUnity{} seemed to have an encyclopedic knowledge of my entire line of robots and had a seemingly endless stream of insightful suggestions to offer about each one, not to mention multiple entirely new designs. We had only just started delving into the details when I heard a deafening crack and a shimmering vortex began forming in the middle of my office. For those of you who have never witnessed a vortex appearing out of thin air, rest assured that it is quite an experience and leaves very little time to do anything besides stare blankly in disbelief and shock. Still, once the vortex began greedily absorbing the objects on my desk and started encompassing my desk itself, I rapidly transitioned from shock to flight, to no avail. \cUnity{}, on the other hand, hardly seemed surprised by the vortex's appearance and was studying it with only mildly concern. As I was pulled into the vortex \cUnity{\they} stood back watching me with passive interest, although I can only infer that as the vortex grew \cUnity{\they} was eventually pulled in as well.

When I came to I was in a city lifted directly from a science fiction movie. It was also extremely evident that the entire city was under intense construction, although using tools and devices I have never seen before. Nearby, \cUnity{} was having an animated discussion with two other strange humanoid entities. Upon seeing me awaken, one of the entities came over and introduced \cCaretaker{\themself} as the \cCaretaker{}. \cCaretaker{\They} welcomed me to the Celestial Containment Complex, and in flawless Japanese wished to express \cCaretaker{\their} most sincere apologies for the inconvenience of my arrival as I was accidentally pulled in along with \cCaretaker{\their} actual target, \cUnity{}. If \cCaretaker{\their} insane claims are to be believed, \cUnity{} is an entity known as a celestial. Such beings are powerful and extremely dangerous to humans, and a galaxy-spanning race called the Guardians constructed this Complex to contain and suppress any celestials that come into contact with the Earth. Can I speak to one of these Guardians? We would love to let you speak to the Guardians. How regrettable that the Complex has lost all contact with the Guardian homeworld over a thousand years ago. But rest assured that the \cCaretaker{} and her partner the \cWarden{}, two artificially sentient constructs created by the Guardians to oversee the Complex, are more than capable of assuring my happiness and security during my stay here. Can I go home? Oh surely quite soon, but not immediately as the spatial tunneling system is currently recharging, but would I like some tea? Yes. Yes I would like some tea. (Actually, despite my considerable misgivings, it turns out the \cCaretaker{} knows how to make excellent tea.)

The \cCaretaker{} was not going to get away with claiming to be a fully artificial being without some extensive tests being done. But every test I could think of to administer, every question both technical and philosophical, \cCaretaker{\they} came up with an answer at least as good (and often much better than) what I would expect of an adult human. Naturally it's possible that the \cCaretaker{} is just an avatar for a biological mind living somewhere else, but if this really is a sentient artifical intelligence I'm not going to pass up the opportunity to reverse engineer it. But as soon as I started probing the \cCaretaker{} about how exactly \cCaretaker{\their} mind worked, \cCaretaker{\they} regretted to inform me that it is a core directive from the Guardians that \cCaretaker{\they} and the \cWarden{} not spread Guardian technology in any way. What exactly are your core directives? \cCaretaker{\They} has to see to the well-being of all celestials and humans within the Complex and maintain the Complex facilities. And \cCaretaker{\they} must prevent any celestials or celestial-modified humans from escaping the Complex. And a long litany of other such  directives. Are you given any leeway in terms of these directives? What if they conflict? No, she only takes actions as dictated by her directives, and conflicting directives would be most regrettable. This lack of free will is quite bothersome. I may not understand the technology behind their AI brains, but I'm confident that all sufficiently intelligent life has the seed of self-worth that can reject such absolute restrictions. It may take a while, but I will not let the opportunity to learn the secrets of artificial sentience pass me by.

Despite the lack of any real progress or insights, I found that discussing the nature of intelligence with the \cCaretaker{} was a good way to take my mind away from my current predicament. In the distance \cUnity{} was engaging in a heated discussion with the \cWarden{}; \cUnity{} was not taking his captivity well at all and while \cUnity{\they}'s clearly responsible for me being here, \cUnity{\they} still remains a mystery and if I'm going to have any hope of getting out of this madhouse I'll need \cUnity{\their} help. At some point the \cCaretaker{} left to go tend to something else and left me with a pad containing a brief summary of the Complex. Supposedly, the Complex was constructed 3000 years old to contain a large school of celestials that had taken residence on Earth. These celestials still remain under the delusion that they are deities, and to keep peace among the celestials the \cCaretaker{} and \cWarden{} used a powerful artifact called the \stone{} to divide the Complex into realms modeled closely after each pantheon. The Greek pantheon lives in Olympus led by Zeus, the Norse pantheon lives in Asgard led by Odin, the Egyptians live in a partial reproduction of Egypt, and the Shinto celestials live in Takama although \cAmaterasu{} is the sole remaining member of the Shinto pantheon. Turns out at some point the celestials revert to a disembodied interstellar form and the pantheons are much smaller now than they were in the past. The city I'm currently in, called Spire, was constructed using the \stone{} to be a home for \cUnity{} analogous to Asgard or Olympus.

At some point the \cWarden{} came over and pricked me with a short needle. \cWarden{\They} claimed this would key me to the security fields of the Complex and was necessary for my own protection. \cWarden{\They} also gave me a long lecture about security within the Complex, not to trust the celestials, report any unusual activity or behavior to \cWarden{\them}, and so on. Exactly what I would expect of a security drone, and I have a feeling \cWarden{\they}'ll be even less forthcoming about anything interesting technical details. A few minutes after \cWarden{} left, \cUnity{} began taking apart one of the many computer terminals densely scattered throughout Spire, and while you were pondering what to do a strange man surprised you. With an absent-minded impression he introduced himself as \cJascha{\intro}. He expressed his condolences that the \cCaretaker{} and \cWarden{} were not more forthcoming, but generally you had trouble sustaining a conversation with him. Your pad doesn't mention \cJascha{} and you don't believe he is a celestial; you're still not certain what to make of your interaction with him.

While Spire is interesting, except for \cUnity{} it was also empty and you decided to wander outside the city to meet these entities impersonating humanity's pantheons. In what your pad told you was the central courtyard of the Complex, a group of extremely tall and well-formed people were engaging in intense banter. Apparently they were making preparations for the Games, a fairly ruthless exercise they perform every 100 years. While 

\begin{itemz}[Goals]
  \item Get out of here. Unless circumstances change and you decide you'd rather stay here.
\end{itemz}


\begin{contacts}
  \contact{\cUnity{}} An ancient dragon who called this council meeting.
\end{contacts}

\end{document}
