\documentclass[char]{guardians}
\begin{document}

\name{\cWarden{}}

\emph{Begin biographical sketch.}

You are the artificially sentient construct W-57129, modeled after the Warden template. In local time, your first moment of existence was 975 BCE where you were brought online by the Guardian \cJascha{\intro} to oversee the Celestial Containment Complex along with a companion construct modeled after the Caretaker template. The Complex was constructed 22 kilometers beneath the surface of the moon orbiting a planet with a primitive but sentient species called humans. The primary function of the Complex is to contain and suppress a species known as celestials and prevent them from interacting with other lifeforms. Shortly after your activation, the Complex's spatial tunneling grid was brought online to transport a large school of such beings that had come into contact with the planet. Due to the fallout of a protracted war of extermination with an aggressive species called the \evilRace{}, the Guardians did not foresee the human-celestial collision and were not able to intervene until several centuries after they first came into contact. During this time the celestials manifested as deities of the indigenous population and caused considerable disruption to their development.

As a Warden, your two primary tasks are to see that order within the Complex is maintained, and that the celestials remain safely contained within the Complex to prevent them from interacting with and harming other species. Fifty-three celestials were originally brought to the Complex from Earth, along with two humans, \cPandora{} and \cEgyptianHuman{}, who had been irreparably modified by the celestials. The first few centuries of containment were turbulent. The celestials, believing themselves to be gods, were enraged at what they perceived as imprisonment by a rival pantheon. Originally, the \cCaretaker{} refused to indulge them in their delusions of godhood, but the imprint of human religion seems permanent. After considerable experimentation the \cCaretaker{} concluded that the only way to preserve their mental sanity was to allow them to indulge in their mythologies to a limited extent. Together you worked with the \cCaretaker{} and \cJascha{} to construct the \stone{}. Using this device you forged four sub-wings within the Complex: Olympus, Asgard, Egypt, and Takama, each modeled closely after their respective mythologies. The celestials were given free reign within their realms, and you found such compartmentalization made it much easier to monitor and manage the celestials.

Extended isolation brought its own set of problems. The leaders of the various factions insisted on the right to prove their superiority over the other factions. You refused to indulge them in this needless disorder for several centuries, although eventually you and the \cCaretaker{} relented when they degenerated to the point where they began defacing their realms and mutilating each other. To try and manage them, the \cCaretaker{} developed the Pantheon Games, where once every century the celestials are allowed to participate in team-building exercises in the central courtyard. In the beginning the celestials were not very receptive, but over time the \cCaretaker{} managed to devised tournaments that successfully relieved some of their aggressive natures.

Matters progressed to an acceptable steady state for a millennia, at which point some celestials begin entering the third phase of their development where they return to their disembodied interstellar form and migrate back to their breeding ground in the Orion Nebula. To avoid the chance that they might come into contact with other sentient lifeforms on their journey to the nebula, such celestials must always be carefully escorted by a Guardian vessel. However, this migration was not well received by the celestials who remain in their second stage within the Complex. Many pantheons believed you were either brainwashing or kidnapping the third-stage celestials. Reacting to this perceived assault, as you predicted the Norse and Greek pantheons both attempted to overpower you. After you successfully put down several such uprisings and the \cCaretaker{} repaired the resulting damage to the systems, things once again settled down as the pantheons shrunk in size.

1500 years ago, \cJascha{} entered the final stage of the Guardian lifecycle. During this period a Guardian's cognitive functions and memory begin to degenerate. Under normal circumstances, such Guardians move to retirement habitats near the Guardian homeworld, but \cJascha{} was granted an unusual request to remain within the complex he designed. Three conditions were imposed for this concession: first, for security reasons and to prevent him from inflicting harm on himself or others, his memory regarding Guardian technology would be erased; second, he would be placed under your direct care as if he were a human; and third, his status as a Guardian would be revoked. \cJascha{} agreed to all these terms and in order to better interact with the local denizens of the Complex the \assembler{} was used to alter his form to look like that of a human. You respect \cJascha{} as an engineer and for his role designing some of your systems, but you also find \cJascha{\them} to be a dangerous security risk. Even with his memory erased, there are still disturbing and unexplained moments where \cJascha{\they} does not show up correctly on your sensor readings.

1000 years ago, you lost contact with the Guardian homeworld. You have had no contact with the homeworld since then, and are continuing to execute the last commands you received. 500 years later when Thor and Set entered stage three, you sent a request for a scoutship but none have arrived. Unable to return home, Set's biochemistry transitioned into an extremely dangerous and unstable state. Realizing his potential to cause damage to the Complex, you voted to use the \assembler{} to terminate him immediately. The \cCaretaker{}, on the other hand, was torn between \cCaretaker{\their} directive to preserve celestials and \cCaretaker{\their} directive to contain them within the Complex. While the \cCaretaker{} was resolving this crisis, you intervened and erected a containment field around the Egyptian realm, but even with these precautions Set's demise resulted in an explosion that caused immense damage throughout the Complex. When Thor also started exhibiting the same biological changes, you were not willing to tolerate a repeat of the Set incident and dragged Thor directly to the \assembler{} where his form was decomposed into its atomic components before he could harm the Complex facilities. The Norse are not aware of all the details of Thor's demise, but they were not pleased about his sudden disappearance and their hostility towards you has been high over the past five centuries. You are keeping a close eye on them in case they attempt to cause another disruption.

The \cCaretaker{} was devastated when you eliminated the threat posed by Thor. In \cCaretaker{\their} distress, \cCaretaker{\they} used \cCaretaker{\their} control over the AI core to modify your core directives to prevent you from killing a celestial under any circumstances. Given that the \cCaretaker{} is absolutely necessary for sustaining the Complex facilities, you are acutely concerned by the stress to \cCaretaker{\their} personality matrix, but you are primarily in charge of keeping order within the Complex and have no ability to assist her. Although the modification to your own personality is within \cCaretaker{\their} authority, you do not like having your security options restricted. In any case it is not likely to do any good --- without the Guardians the stage-three celestials are going to die, either in a dangerous explosion (if you cannot convince the \cCaretaker{} to revert your directives) or in a safe if regrettable way using the \assembler.

\emph{End biographical sketch. Begin daily log analysis.}

Two days ago your sensors detected a new celestial calling itself \cUnity{} on the Earth's surface. In order to mitigate the turbulence caused in the past by new arrivals and make \cUnity{} feel at home, the \cCaretaker{} insisted on activating the \stone{}. You were not thrilled at the idea of activating the stone when the Complex systems are already stressed, but you also do not wish to further stress the \cCaretaker{}'s personality. Together, you began building Spire, a technological city calibrated to align with \cUnity{}'s paradigm. The \cCaretaker{} also allowed the other celestials into the central courtyard to begin the Games 30 years early, in the hopes that the Games would serve as a suitable team-building exercise for \cUnity{}.

Once the city's construction was underway and the preparations for the Games had begun, you activated the spatial tunneling system to transport \cUnity{} to Spire. A small complication occurred and another human named \cKachiko{\intro} was brought along with \cUnity{}. As with the other humans in the Complex, you keyed the forcefield system to protect her from the other celestials. The \cCaretaker{} began counseling procedures for \cKachiko{}, while you turned your attention to \cUnity{}. Unlike the other celestials, who are rooted in mythology and are easy to control with Guardian technology, \cUnity{}'s paradigm is more closely aligned to that of the Guardian's and hence of greater concern. You fear that \cUnity{} may over time be able to undermine the Complex's systems despite the considerable safeguards you have implemented. \cUnity{} has also made no secret of \cUnity{\their} desire to escape confinement. While at present your simulations suggest you will be able to contain \cUnity{}, things are dangerous for the next four hours as the bubble surrounding the Complex reseals itself after being temporarily punctured to permit Unity's transportation. Worse yet, \cUnity{} may attempt to recruit other celestials to help \cUnity{\them} escape.

While the \cCaretaker{} went to continue preparations for the Games, you returned to the control chamber to oversee the resealing of the bubble and the Pantheon Stone's containment field. But as you continued monitoring the situation, a cascade of system failures occurred. Immediately moving to diagnose the problem, you were unable to ascertain the source with any certainty; none of the failures were critical and you soon restored most functionality. But soon thereafter, the sensors for a brief moment registered trace quantities of an extremely rare isotope called Kisrin. Although not itself dangerous, it is very time consuming to manufacture and it sits at the threshold of Guardian technology --- there is no way it could have come from Earth and it cannot be manufactured within the Complex. And as you are positive there are no traces of Kisrin used in any of your facilities, you have no explanation for how it could appear on your sensors and why it has just as quickly vanished. Your two best hypotheses are that either \cUnity{} is more than \cUnity{\they} appears to be, or there is someone else within the Complex with Guardian-level technology. Both possibilities greatly concern you and given that Complex security may be compromised, investigating the Kisrin observation is one of your highest priorities.

Once you restored system functionality, you were alerted to critical errors within Spire. Apparently, \cUnity{} had taken advantage of (and possibly caused) the brief moment of chaos and used it to seize control of Spire's security grid to restrict you and the \cCaretaker{} from entering the city. Normally this would be of immense concern, but you expected just such an eventuality and designed Spire's control network so that it is completely isolated from the rest of the Complex systems. Although still troublesome and you intend to regain access to Spire momentarily, you are confident that \cUnity{} will not be able to leverage \cUnity{\their} control over Spire to compromise any additional systems.

%Warden wants to kill all the celestials rather than allowing them to escape. Big contrast from caretaker.
%Only Unity can learn how to ``remove celestialness''.  The AIs can't do it.
%Geb is dead, but the Caretaker doesn't know about it at game start.

\emph{End daily log analysis. Begin current state evaluation.}

Unlike the \cCaretaker{}, you are not susceptible to the dangers of empathizing with the celestials. They are dangerous beings that have caused immense damage throughout the galaxy. The Celestial Containment Complex was built for precisely this reason, and although they are living beings, the celestials must remain contained at all costs. Even a single celestial escaping to Earth has the potential to destabilize the entire civilization, and you would rather see the entire Complex destroyed than allow a single celestial to escape.

Your analysis of the current situation shows matters to be mostly in hand. \cUnity{} is capable but you will restore control of Spire soon, and in four hours the bubble will safely reseal itself around the Complex. \cKachiko{}'s presence here is regrettable and \cKachiko{\they} is talented for a human scientist but still incapable of affecting matters. Your greatest concern is the stage-three celestials. You know from the experience with Set and Thor that their potential to damage the Complex is high, and it is a core directive given by the Guardians to both you and the \cCaretaker{} that without the escort of a Guardian ship, celestials cannot be freed for any reason. The \cCaretaker{} has prevented you from resolving the problem through demolecularization, although you realize \cCaretaker{}'s personality matrix suffers severe damage each time a celestial dies. The \cCaretaker{} is in charge of maintaining the Complex and it cannot function without the both of you.

The various existing pantheons are for the most part reacting to \cUnity{} as a pleasant diversion from the usually boring state of affairs. Zeus and Odin are, as usual, in an angry dispute and are dragging their pantheons into the conflict. Your limited eavesdropping indicate that Anubis, Osiris, Isis, and their human companion \cEgyptianHuman{} have been discussing Set's demise, which suggests they may be planning trouble. \cJascha{} is performing his characteristic wandering between the pantheons and appears pleased by \cUnity{}'s arrival and the recent activity. The Norse are currently the faction that concerns you the most, as they have not yet reacted as strongly as you expected to Thor's disappearance and you suspect they are planning something serious. But riding on top of all these concerns is the unexplained Kisrin incident, which you fear might be an indication of a potentially fatal breach in Complex security, and without any contact from the Guardians you are the last line of defense to keep the celestials from wreaking havoc on Earth.

TODO: PANDORA-POWER-STEALING

\emph{End current state evaluation. Executing action planning.}

\begin{itemz}[Notes]
  \item \textbf{Psychlim} --- You are an artifical construct created by the Guardians. You cannot take any actions that knowingly violate your Core Directives.
\end{itemz}

\begin{itemz}[Core Directives]
  \item Fulfill your role as warden of the Complex. Preserve order among the celestials and oversee the security of the Complex.
  \item Work with the Caretaker to keep all celestials and celestial-modified humans contained within the Complex to prevent future harm to other species. Celestials entering stage three may only leave the Complex if escorted by a verified Guardian ship.
  \item Preserve the state of affairs on Earth at any cost; do not allow communication with the human population or allow Guardian technology or celestials to disrupt the Earth's development.
	\item Do not kill any celestials or use the \assembler{} to modify a celestial such that they can be killed. \emph{This directive was appended by the \cCaretaker{}.}
  \item Obey any future directives that are verified to come from the Guardians.
\end{itemz}

\begin{itemz}[Derived Goals]
  \item Investigate the Kisrin observation and deal with any security ramifications.
  \item Keep a close eye on all celestials to prevent them from escaping or causing a disruption. Unity is very vocal about \cUnity{\their} desire to escape, and the Norse are still angry over Thor.
  \item Prevent the celestials from penetrating the field protecting the \stone{} and trying to use it themselves.
  \item Restore control over Spire's computer system.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} Your counterpart. In charge of the mental and physical well-being of the Celestials and the maintenance of all Complex facilities.
  \contact{\cJascha{}} The chief Guardian engineer who designed you and the rest of the facilities. Currently in the last stage of his life and is genetically a human and under your care.
  \contact{\cUnity{}} A dangerous celestial who is obsessed with technology and who you just transported to the Complex.
  \contact{\cKachiko{}} A standard human who was accidentally brought through with \cUnity{}.
\end{contacts}

\end{document}
