\documentclass[blue]{guardians}
\begin{document}

\name{\bWhosWho{}}

The Complex has been in operation for over 3000 years. Its custodians, the \cCaretaker{} and \cWarden{}, claim that the Complex was created by a group called the Guardians, who believe the gods to be a starfaring species called celestials. The Guardians captured the celestials on the Earth and transferred them to the Complex, creating the \cCaretaker{} and the \cWarden{}.

Over the past 2000 years, many celestials have been willingly escorted out of the Complex by Guardian ships, and consequently the size of the pantheons has slowly dwindled. This changed 1000 years ago, when all contact with the Guardians was lost. 500 years ago, Thor and Set vanished and a large explosion shook the Complex.

The residents of the Complex have been living with each other for thousands of years and are very familiar with each other.

\begin{itemz}[The Founders]
\item \cWarden{} --- A powerful artificial construct who enforces security within the Complex.
 \item \cCaretaker{} --- The counterpart to the \cWarden{} who tries to see to the well-being of the celestials.
 \item \cJascha{} --- A human who came to the Complex thousnads of years ago and resides within the Complex. Unlike most residents, \cJascha{\they} can move freely between the realms.
\end{itemz}

\begin{itemz}[Greek Pantheon]
  \item \cZeus{} --- The ruler of Mount Olympus, the god of thunder and the sky.
  \item \cHera{} --- The wife of Zeus, the goddess of women and marriage.
  \item \cAthena{} --- Daughter to Zeus and Metis, the goddess of wisdom and courage.
  \item \cHephaestus{} --- The son of Hera, god of fire, metalworking, and sculpture.
  \item \cPandora{} --- A human created by Hephaestus and Athena.
\end{itemz}

\begin{itemz}[Norse Pantheon]
  \item \cOdin{} --- The ruler of Asgard, ancient enemy of the frost giants of Jotunheim.
  \item \cHel{} --- The Norse ruler of the dead.
  \item \cFenrir{} --- A wolf in human form who was created by the Norse.
  \item \cVal{} --- A valkyrie tasked with bringing chosen warriors to Valhalla.
\end{itemz}

\begin{itemz}[Egyptian Pantheon]
  \item \cIsis{} --- The mother of Egypt and the patroness of nature and magic.
  \item \cAnubis{} --- The Guardian of the Scales, who protects the dead during their journey into the afterlife and weighs their heart against Maat's feather.
  \item \cOsiris{} --- The god of the afterlife, who rules over the dead.
  \item \cEgyptianHuman{} --- A human created by Osiris and Isis.
\end{itemz}

\begin{itemz}[Shinto Pantheon]
  \item \cAmaterasu{} --- The goddess of the sun and the universe. She is the sole resident of Takama, and accepted by the gods as the arbiter the Pantheon Games.
\end{itemz}

\begin{itemz}[New Arrivals]
  \item\cUnity{} --- A powerful being from the modern technological age, who arrived only an hour ago. The \cCaretaker{} created Spire, a large industrial city, for Unity to live in.
  \item\cKachiko{} --- A human who arrived with Unity.
\end{itemz}

\end{document}
