\documentclass[green]{guardians}
\begin{document}

\name{\gAspect{}}

Some characters in game have one or more Aspects representing their inherent powers or attributes. Aspects are required by various mechanics, and can be used to increase a player's skill at various competitions. Once during each hour of game, you may use one of your Aspects. You can reuse the same Aspect during different hours of game. You may also have abilities that allow you to use Aspects under other conditions.

\TODO{Does using an Aspect as a buff require taboo?}

\TODO{What are the Olympic games actually called?}

Using an Aspect requires playing two games of Taboo, which is described below. Your Aspect is not used until you start playing the second game. After the first game, you can decide not to continue, keeping your Aspect. If you decide not to commit to the second game, you can later change your mind and play the second game at any time.

\TODO{What if a player needs their own Aspect?}

\section*{Playing Taboo}

% Modified from Year 7 rules for taboo.
If you need an Aspect for a mechanic, you must get a player who has the Aspect to guess a specified word or phrase without using the word or phrase itself or any of the words indicated as forbidden. Don't use forms or parts of any of the words, either. If you accidentally use a forbidden word, tell the player the word or phrase you were trying to have them guess, and restart the game using one of the backup words provided.

The words or phases which must be guessed will have some connection to whatever you need the Aspect for. The second game of Taboo will generally have a more revealing word or phrase than the first game.

\TODO{Maybe just put this in rules-scenario instead; everyone needs to know that taboo words are clues about plot.}

\end{document}
