\documentclass[green]{guardians}
\begin{document}
\name{\gReassembler{}}

The Molecular Reassembler is a device developed by the Guardians. It is a large container that can easily accommodate a human body, and is designed to modify the molecular structure of whatever is placed within the vessel. The device is very versatile, with the most readily available settings provided below.

Using the Molecular Reassembler requires the \aGuardianTech{} ability and an Aspect. To start the device, the recipient must be restrained in the chair. They do not have to be willing or conscious, and do not need to be told which setting you are using. Then you or someone else must invoke one of the listed Aspects on your behalf. You must spend at least one minute interacting with the device. When you finish, tell the recipient to open the packet listed after each setting.

\subsection{Settings}

\begin{itemize}
  \item \textbf{Enhance Genetic Structure; Aspect of Eternity, Power, or Motherhood; $\Gamma$ packet} --- Significantly enhances the genetics of a human, granting vastly improved health and longevity along with enhanced intelligence, agility, and strength. Has no effect on celestials.
  \item \textbf{Celestial Suppression; Aspect of Protection, War, or Destruction; $\Gamma$ packet} --- Permanently and irrecoverably destroys key components of the celestial biological cycles. This will freeze a celestial in its current form, preventing further life stages from occurring. Guardian protocols specifically prohibit this type of intervention in the lifecycle of other species, considering it to be equivalent to murder or forced castration. Has no effect on non-celestials.
	\item \textbf{Human Reversion; Aspect of War, Mortality, or Justice; $\Gamma$ packet} --- Permanently and irrecoverably turns a celestial into a mortal human, eliminating all of their celestial abilities and immunities. Has no effect on non-celestials.
	\item \textbf{Demolecularization; Aspect of Death, Destruction, or Vengence; $\Omega$ packet} --- Breaks everything in the vessel down into its molecular components. The recipient should immediately go "NOT HERE", and find a GM, taking their items with them.
		\item \textbf{Resurrection and Rebirth; Aspect of UNKNOWN; $\Omega$ packet} --- A deceased human corpse may be brought back to life, so long as they died within the past 30 minutes. CARETAKER ONLY?
	
\end{itemize}

If you gain an ability starting with "Molecular Ressembler Setting", you may use that setting on the Molecular Ressembler so long as you still have the \aGuardianTech{} ability.

\end{document}
