\documentclass[char]{guardians}
\begin{document}

\name{\cAmaterasu{}}

You are Amaterasu who shines in the heaven, the goddess of the sun and the universe, the daughter of Izanagi, the sister to Susanoo and Tsukuyomi. You also find yourself to be the very last of the kami. Although you intend to continue watching over the Earth and its scattered peoples for as long as you can, you admit to yourself that it is lonely with your family having long since dispersed among the many stars.

Long ago, you and your siblings walked with the Japanese people throughout their long history. Your people suffered when your family had its rivalries and prospered through your fleeting moments of joy. But that was all in the distant past. At some point, you and your family were pulled through a powerful vortex by an entity called the \cWarden{}. Ever since then you have been living in a bubble, disconnected from the Earth but still able to watch humanity's troubles. There are other gods in the bubble with you from other places, most of whom perceive this to be a grand prison they must fight tooth and nail to escape from. You feel differently --- human-made troubles like pollution or deforestation are nothing compared to the damage that could be caused by the likes of Odin or Zeus being unleashed on the Earth. Since the greatest dangers to humanity reside in this strange bubble with you, your charge is to remain here as well to watch over the other gods.

Time moves differently for the kami, but it still moves. When you first arrived, a being called the \cCaretaker{} welcomed your whole family to the Celestial Containment Complex and moved you into a facsimile of Takama-ga-hara, the plain of high heaven. Here you resided for your stay here, while the other gods from other pantheons resided in realms modeled after their ancestral homes. Like the Greeks and the Norse, your family did not take well to its captivity at first, but over the centuries things settled down. But one day, your brother Susanoo felt the call to move beyond this world to the next one. The \cCaretaker{} and \cWarden{} escorted him to a great ship that carried him into the stars. Over the intervening years, the rest of your family slowly felt the call and eventually they too were all similarly escorted away. Gods from other pantheons similarly felt the desire to travel the stars, although many resisted their lure with little success. Still, things changed a thousand years ago when the \cCaretaker{} and \cWarden{} lost contact with their creators the Guardians. Ever since contact was lost, no great ships have arrived to carry gods into the stars and the \cWarden{} will not permit any gods to leave without such an escort. This problem reached its peak when Thor and Set felt the call. Eventually, Set was angered at his continued captivity to the point where he exploded in a violent burst of energy felt throughout the realms, and Thor mysteriously vanished. But things in the complex have otherwise been quiet for the last 500 years.

Normally, you spend your time within Takama in solitude. Occasionally, you have visits from the \cCaretaker{} or \cWarden{} who have granted you a viewing portal from which you can watch events on Earth unfold. You also have occasional visits from a strange young man called \cJascha{\intro}. You are not really sure what his role in the Complex is, as he appears to be in every way human but hasn't aged in a thousand years. Unlike all the other residents, \cJascha{} is able to move freely between the realms of the gods. You suspect he was involved in this prison's creation, but he does not seem to be able to remember any details from his past.

Every one hundred years, the \cCaretaker{} brings all the gods to the central courtyard for what \cCaretaker{\they} refers to as a team-building exercise called the \pGames{}. You find the other gods to provide a very different perspective but they are also fickle, capricious, and take actions with absolutely no regard for the consequences. While you are content to be left to your contemplations in Takama, the other gods appear to thirst for each other's blood and need to prove their superiority over each other like adolescent boys. Although the Shinto pantheon used to participate as well, this stopped once you became the only remaining member. Instead, the Greek and Norse pantheons petitioned you to take over as the arbiter of the games from the \cCaretaker{}. You find the games to be an odd contrivance, but you silently enjoy your role as a judge and believe you do quite a good job at it even if it feels like managing a horde of rowdy children.

The other gods reside under the delusion that the \cCaretaker{} and \cWarden{} are members of a rival pantheon, out to punish and control them, and they cannot accept the implications of a star-spanning race like the Guardians. But you are the goddess of the universe, and your perspective is vast. You understand that the Guardians are a race with strengths and flaws not unlike humans, and that this Complex and the \cCaretaker{} and \cWarden{} the Guardians conscripted to oversee it are simply finite constructs, not some shard of divine beings. These constructs were designed for a very specific task, and the Guardians did not grant them the leeway to adapt to unforseen situations.

Today this endless cycle of contemplation interrupted by the occasional Games was abruptly interrupted. The \cCaretaker{} summoned everyone to the courtyard to announce the imminent arrival of \cUnity{}, a new kami from the modern age. The \cCaretaker{} placed you in charge of organizing an impromptu version of the Games to welcome \cUnity{} to \cUnity{\their} new home. The \cCaretaker{} and \cWarden{} then took the \stone{} and left to prepare for Unity's arrival. This round, the gods seem quite intent on taking the Games very seriously and have wagered three items of immense power on the outcome of the games. The \cCaretaker{} has secured these items and will release them when you announce the winning pantheons at the conclusion of the Games in three hours.

You agree with the Warden, gods are dangerous.

\begin{itemz}[Goals]
  \item Z.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} An ancient dragon who called this council meeting.
\end{contacts}

\end{document}
