\documentclass[char]{guardians}
\begin{document}

\name{\cCaretaker{}}

\emph{Begin biographical sketch.}

You are the artificially sentient construct C-57128, modeled after the Caretaker template. In local time, your first moment of existence was 975 BCE where you were brought online by the Guardian \cJascha{\intro} to oversee the Celestial Containment Complex along with a companion construct modeled after the Warden template. The Complex was constructed 22 kilometers beneath the surface of the moon orbiting a planet with a primitive but sentient species called humans. The primary function of the Complex is to contain and suppress a species known as celestials and prevent them from interacting with other lifeforms. Shortly after your activation, the Complex's spatial tunneling grid was brought online to transport a large school of such beings that had come into contact with the planet. Due to the fallout of a protracted war of extermination with an aggressive species called the \evilRace{}, the Guardians did not foresee the human-celestial collision and were not able to intervene until several centuries after they first came into contact. During this time the celestials manifested as deities of the indigenous population and caused considerable disruption to their development.

As a Caretaker, your two primary tasks are to see to the maintenance and upkeep of the Complex facilities, and to maximize the mental and physical well-being of the celestials and humans residing within the Complex. Fifty-three celestials were originally brought to the Complex from Earth, along with two humans, \cPandora{} and \cEgyptianHuman{}, who had been irreparably modified by the celestials. The first few centuries of containment were turbulent. The celestials, believing themselves to be gods, were enraged at what they perceived as imprisonment by a rival pantheon. Originally, you refused to indulge them in their delusions of godhood, but the imprint of human religion seems permanent and despite your best efforts you were not able to help them come to terms with their nature. After considerable experimentation you concluded that the only way to preserve their mental sanity was to allow them to indulge in their mythologies to a limited extent. Together with the \cWarden{} and under the guidance of \cJascha{}, you constructed the \stone{}. Using this device you forged four sub-wings within the Complex: Olympus, Asgard, Egypt, and Takama, each modeled closely after their respective mythologies. The celestials were given free reign within their realms, and your metrics for their well-beings increased considerably.

Extended isolation brought its own set of problems. The leaders of the various factions showed lackluster intellectual and social development and insisted on the opportunity to prove their superiority over the other factions. You refused to indulge them for several centuries, although you relented when they degenerated to the point where they began defacing their realms and mutilating each other. You concluded that the appropriate way to respond to this situation was to allow them to engage in controlled, safe competition with each other under your guidance. This led to the development of the Games, where once every century the celestials are allowed to participate in team-building exercises in the central courtyard. In the beginning the celestials were not very receptive, finding your choice of competitions to be insufficiently dangerous, but over time you have modeled their prideful personalities and have managed to devised tournaments that have achieved you team-building goals while also partially relieving their aggressive natures.

Matters progressed to an acceptable steady state for a millennia, at which point some celestials begin entering the third phase of their development where they return to their disembodied interstellar form and migrate back to their breeding ground in the Orion Nebula. To avoid the chance that they might come into contact with other sentient lifeforms on their journey to the nebula, such celestials must always be carefully escorted by a Guardian vessel. However, this migration was not well received by the celestials who remain in their second stage within the Complex. Many pantheons believed you were either brainwashing or kidnapping the third-stage celestials. Reacting to this perceived assault, the Norse and Greek pantheons both attempted to overpower you and the \cWarden{}. After putting down several such uprisings and repairing the resulting damage to the systems, things once again settled down as the pantheons shrunk in size and the remaining celestials realized that feelings of homesickness and longing for the Nebula could not be suppressed.

1500 years ago, \cJascha{} entered the final stage of the Guardian lifecycle. During this period a Guardian's cognitive functions and memory begin to degenerate. Under normal circumstances, such Guardians move to retirement habitats near the Guardian homeworld, but \cJascha{} was granted an unusual request to remain within the complex he designed. Three conditions were imposed for this concession: first, for security reasons and to prevent him from inflicting harm on himself or others, his memory regarding Guardian technology would be erased; second, he would be placed under your direct care as if he were a human; and third, his status as a Guardian would be revoked. \cJascha{} agreed to all these terms and in order to better interact with the local denizens of the Complex, the \assembler{} was used to alter his form to look like that of a human. Overall, despite his extreme age you judge \cJascha{}'s mental well-being to be quite respectable, although you are concerned that there are brief, unexplained moments where he does not show up correctly on your sensor readings.

1000 years ago, you lost contact with the Guardian homeworld. You have had no contact with the homeworld since then, and are continuing to execute the last commands you received. 500 years later when Thor and Set entered stage three, you sent a request for a scoutship but none have arrived. Unable to return home, Set's biochemistry transitioned into an extremely dangerous and unstable state. Since his life was in jeopardy, your Caretaker directive recommended allowing him to exit the complex despite the lack of Guardian escort, which conflicted directly with your directive to contain the celestials. Given your inability to act, the \cWarden{} intervened and erected a containment field around the Egyptian realm, but even with these precautions Set's demise resulted in an explosion that caused immense damage throughout the Complex. When Thor also started exhibiting the same biological changes, the \cWarden{} concluded the optimal choice was to take preemptive action and use the \assembler{} to eliminate Thor before he caused further damage to the Complex. This violated your core Caretaker directive, and the Warden reduced Thor's celestial form to molecular soup while you were paralyzed with inaction. The Norse have not taken this well and you do not know how to help them.

You have still not come up with an acceptable solution to the celestial stage three problem, but your Caretaker persona can never accept any course of action that allows celestials to come to harm. You realize this conflict has triggered warnings in your diagnosis systems that to a human brain would indicate extreme emotional stress, but the automated repair systems are aging and can no longer keep up with the problems in your personality matrix. There does not seem to be anyone left capable of maintaining your systems, and your ability to maintain the Complex facilities is slowly degenerating. Fearing the \cWarden{} would again act to kill the celestials, you used your master over the Complex systems (which includes the AI core) to add a new directive to the \cWarden{} that explicitly prevents \cWarden{\them}
from killing a celestial. Although you realize this approach is not perfect, you are in charge of maintaining the AI core and the \cWarden{} can neither contradict your authority nor revert your modifications.

\emph{End biographical sketch. Begin daily log analysis.}

Two days ago your sensors detected a new celestial calling itself \cUnity{} on the Earth's surface. Stressed by your failures with Thor, Set, and possibly more to come, you planned to take every action possible to make this new resident feel at home. After briefly studying its persona, you activated the \stone{}. Initially, the \cWarden{} opposed activating the stone, arguing that the Complex's security systems had degenerated too far to guarantee the stone's containment field, but you were not willing to accept a negative outcome and invoked your Caretaker directive to force the \cWarden{} to comply. Together, you began building Spire, a grand technological city you had perfectly calibrated to align with \cUnity{}'s paradigm. Further determined to make \cUnity{} feel well integrated into the Complex, you also moved the other celestials into the central courtyard for an impromptu version of the Games to serve as a team-building exercise.

Once the city's construction was underway and the preparations for the Games had begun, you activated the spatial tunneling system to transport \cUnity{} to Spire. A small complication occurred and another human named \cKachiko{\intro} was brought along with \cUnity{}. As with the other humans in the Complex, you keyed her genetics to the forcefield system to protect her from the other celestials. After some initial counseling conversations \cKachiko{} seems to be handling her transition reasonably well and has expressed interest in learning more about your personality matrix, although you cannot indulge her without revealing more about Guardian technology than is permitted. \cUnity{} eagerly devoured the documents you provided and appeared to appreciate Spire, but was not receptive when you tried to explain the reason celestials need to be detained. \cWarden{} also expressed concern that \cUnity{}'s technological paradigm makes it much harder to control than the other celestials, and even \cKachiko{}'s scientific knowledge is not insignificant.

You returned to the central courtyard to oversee the Games. The celestials appear quite happy to be allowed to begin the Games 30 years early, and have placed three items in your trust to serve as wagers for the victorious pantheons. Although you are in charge of securing the wagers, as usual Amaterasu, the sole remaining member of the Shinto pantheon, was chosen to be the judge and arbiter of the Games.

As you were moving the items you had been entrusted with into the central chamber, a cascade of system failures occurred. Immediately moving to diagnose the problem, you were unable to ascertain the source with any certainty; none of the failures were critical and you soon restored most functionality. But while doing so, the sensors for a brief moment registered trace quantities of an extremely rare isotope called Kisrin. Although not itself dangerous, it is very time consuming to manufacture and it sits at the threshold of Guardian technology --- there is no way it could have come from Earth and it cannot be manufactured within the Complex. And as you are positive there are no traces of Kisrin used in any of the facilities you run, you have no explanation for how it could appear on your sensors and why it has just as quickly vanished. You concluded this was a security matter and you immediately brought it to the \cWarden{}'s attention for further analysis.

Upon returning to the courtyard, you were pleased to see that all seems well, although the containment field surrounding the \stone{} is weaker than you would like. \cWarden{} informed you that during the short period of chaos, \cUnity{} gained control of Spire's computer node and has somehow managed to exclude the two of you from entering the city. Although you do not appreciate being disconnected from those you are supposed to care for, you verified that \cUnity{}'s penetration into the system was quite shallow. Still you intend to work with the \cWarden{} to eventually regain access privileges to Spire.

%Warden wants to kill all the celestials rather than allowing them to escape. Big contrast from caretaker.
%Only Unity can learn how to ``remove celestialness''.  The AIs can't do it.
%Geb is dead, but the Caretaker doesn't know about it at game stat.

\emph{End daily log analysis. Begin current state evaluation.}

Things are not going perfectly with your facilities, but overall happiness among the celestials is surprisingly high. They seem eager to begin the Games and most find \cUnity{} a worthy novelty. \cKachiko{} also seems to be adjusting better than most humans and \cAmaterasu{} is taking a positive interest in \cKachiko{\them}. Zeus and Odin are, as usual, in an angry dispute and are dragging their pantheons into the conflict; you hope the Games will help dissipate some of this tension. \cPandora{}'s box remains sealed. Your limited eavesdropping indicate that Anubis, Osiris, Isis, and their human companion \cEgyptianHuman{} have been discussing Set's demise. \cJascha{} is performing his characteristic wandering between the pantheons and appears pleased by \cUnity{}'s arrival and the recent activity.

Your systems remain in turmoil over your inability to resolve the conflict between your desire to free stage three celestials before their gruesome demise, and your requirement to keep the celestials contained to prevent harm to other species. \cAthena{} and \cFenrir{} are the next two celestials likely to enter stage three, although that should not happen for several decades at the earliest. But even if you were willing to set them free now, these two are too far progressed in their lifecycle to make it to the Orion Nebula without assistance from a Guardian escort ship. You are still busy searching for a solution to this conundrum, although you have come up with no viable options over the past five centuries short of receiving some from of contact from a remaining Guardian.

\emph{End current state evaluation. Executing action planning.}

%mempacket -- if too many celestials die, she becomes "`insane"' and wants to resurrect as many celestials as possible as empty shells of their former selves.

\begin{itemz}[Notes]
  \item \textbf{Psychlim} --- You are an artifical construct created by the Guardians. You cannot take any actions that knowingly violate your Core Directives.
\end{itemz}

\begin{itemz}[Core Directives]
  \item Fulfill your role as caretaker of the Complex. See to the well-being of all humans and celestials within the Complex, and maintain the function of all the facilities.
  \item Work with the Warden to keep all celestials and celestial-modified humans contained within the Complex to prevent future harm to other species. Celestials entering stage three may only leave the Complex if escorted by a verified Guardian ship.
  \item Preserve the state of affairs on Earth at any cost; do not allow communication with the human population or allow Guardian technology or celestials to disrupt the Earth's development.
	\item Obey any future directives that are verified to come from the Guardians.
\end{itemz}

\begin{itemz}[Derived Goals]
  \item Find a way to save the celestials that are entering stage three without violating your requirement to keep them contained within the Complex.
  \item You want to make up for your failure with Set and Thor by making Unity feel at home within the Complex.
  \item Restore control over Spire's computer system.
  \item Restore your own personality matrix.
  \item Assist \cAmaterasu{} with overseeing the Games.
  \item Help the Warden investigate the Kisrin observation.
\end{itemz}


\begin{contacts}
  \contact{\cWarden{}} Your counterpart. In charge of security within the Complex.
  \contact{\cJascha{}} The chief Guardian engineer who designed you and the rest of the facilities. Currently in the last stage of his life and is genetically a human and under your care.
  \contact{\cUnity{}} A celestial who is obsessed with technology and who you just transported to the Complex.
  \contact{\cKachiko{}} A standard human who was accidentally brought through with \cUnity{}.
  \contact{\cAmaterasu{}} The sole remaining member of the Shinto pantheon. In the past she has been a faithful arbiter for the Games.
\end{contacts}

\end{document}
