\documentclass[char]{guardians}
\begin{document}

\name{\cFenrir{} (En-ust'ae C'ny'zae)}

You were only a child when the Guardians destroyed your home world. There was complete chaos when the Guardian fleet arrived and began bombardment. You were one of the few who escaped, because you were already on board a star ship in orbit. Billions of other Undoth were not so lucky. Your home world was obliterated, and with it, most of your race's civilization, technology, and slaves.

For almost a millenium the Undoth were on the run, trying to hide their existence from the Guardians. Eventually, you decided that life didn't suit you. You left in your a shuttle to follow a group of migrating Celestials to a far corner of the galaxy.

These Celestials are beings of energy which seek out worlds inhabited with intelligent life, and take on a form based on the inhabitants' thoughts, appearance, and ways. Once the Celestials take on a species' form, they forget what they really are, until they reach the point in their life cycle where they begin to yearn for home. Then they migrate back to the galactic core to reproduce.

Like the Celestials, Undoth have the ability to change their form. However, for beings who are not made of energy, it takes more time. When you arrived with the Celestials on the planet called ``Earth,'' you spent a year in a cocoon transforming your biology to be like one of the native animals you felt a natural affinity for---a wolf. You emerged to find the Celestials had become gods to the humans. There were Odin, Tyr, and many others. As you grew and came into conflict with the Celestials and humans, you became part of the humans' mythology as Fenrir, the monster of the river V\'an.

The humans would make ideal slaves for the Undoth: they're intelligent, but physically weak compared to you, and many are subservient by nature. Given time, their technology would advance far enough that you could gather a force of star ships manned by human slaves and rejoin the fight against the Guardians.

However, you didn't have time. The Guardians' meddling extends even to this far corner of the galaxy. When the Guardians got wind of the Celestials on Earth, they built a containment complex for Celestials on the planet's moon, operated by two AI, the \cWarden{} and the \cCaretaker{}. Then they forcibly teleported the Celestials and you (mistaken for a Celestial) to the complex. And now, millenia after your home world was destroyed, you're in the power of the Guardians once again. You have bided your time, waiting for a way to escape back to Earth. Life in the complex is boring for you; only the competitions your overseers hold once a century and your plans to escape keep it from being completely dull. At least your supervisors still think you're a Celestial.

You don't really enjoy the company of most of the Celestials. Most of them are arrogant. Some of them have the ridiculous idea that it's their responsibility to care for the humans. \cAnubis{} is the only one you could call a friend. Like you, [...]
% Also very Lawful Neutral
% Okay with you enslaving the humans
% Not likely to have any issue with you being Undoth

Over time, more and more of the Celestials imprisoned in the complex have reached the next stage of their life cycle, where they begin to yearn for home. Whenever that happens, the \cWarden{} and \cCaretaker{} send the Celestials in question away on a Guardian ship, which you assume takes them back to the galactic core. However, 500 years ago, when \cSet{} and Thor began to yearn for the stars, something went wrong. You can only assume the Guardian ship never came. The two Celestials remained in the complex, gradually losing their sanity, while the \cWarden{} and the \cCaretaker{} had heated arguments when they thought you weren't around. In the end, there was a massive explosion in the complex, and you were told it had killed \cSet{} and Thor. Celestials can explode if they don't reach the galactic core in time; you guess that must have happened to one of the them, killing both. You must keep that speculation to yourself, of course, because the Celestials wouldn't know it.

Athena is the only Celestial who is currently yearning for home. At least she's far from the stage where there's any risk she'll go critical. You're not even sure the complex could survive another explosion like the last one. In recent times you've started pretending to long for the stars yourself, in the hope that it will give you an opportunity to escape. Although, given that no Guardian ship arrived to transport \cSet{} and Thor, you don't hold out too much hope. Your fellow Norse have a more ambitious plan to get out of the complex: They want to rebuild the Bifrost bridge, and use it to travel to Jotunheim to bring down the frost giants. You have no desire to spend your life fighting frost giants, but you'll happily help Odin, Hel, and \cVal{} build the Bifrost if it means they'll be of your way. Then Earth will be free for the taking. You can't let the others know that's your plan, however; they seem to actually care about the humans.

You and \cVal{} have spent some time with Athena ever since you began pretending to long for the stars. Of course, between the games every century, you can only communicate by sending messages to each other through \cJascha{}, who is allowed to wander between the different pantheons' realms. \cJascha{} appears to be an old human, but you suspect he's actually a Guardian. He seems harmless, but you always take extra care around him to avoid doing anything which would give away that you're actually an Undoth, not a Celestial.

Athena is more intelligent than most of the Celestials here; she's accepted that she's a Celestial, and is worried about what will happen if no Guardian ship arrives in time to take you and her back to the galactic core. With her, you're building an interstellar radio. Some of the Undoth technology which you managed to sneak with you into the complex will make this much easier, but you have to keep it hidden from \cJascha{} and the AI. As far as Athena is concerned, the purpose of the radio is to contact the Guardians directly in a desperate attempt to get them to send a ship. However, you also plan to broadcast a signal to let the rest of the Undoth know where you are.

\TODO{The stolen device might need a more specific description}

% TODO: This might be a weapon which can only be used with knowledge from Fenrir.
% It might also be a component used to make a weapon.
A few months ago, one of your Undoth devices disappeared. Not something you need to construct the radio, fortunately, but you're scared that it will fall into the hands of one of the AI or \cJascha{}, who would recognize its Undoth origin. It must have been one of the Norse who took it, since it happened between games when you're restricted to your own realms, but if you make a fuss about it your overseers are more likely to find out. So far no sign of it has turned up.

In the past day things have started to get busy. For the first time since you were originally imprisoned, a new Celestial has been brought to the complex. This Celestial, \cUnity{}, shows the influence of technology far beyond what the humans had when you were on Earth. You suspect that space flight is not far out of their reach. One consequence of a Celestial influenced by this level of technology is that \cUnity{\they} can actually pose a minor threat to the Guardians. \cUnity{}'s arrival disrupted the complex temporarily, and during the confusion you took the opportunity to scrounge through the complex's computer systems. It turns out that the complex has had no contact with the Guardians whatsoever for more than half a millenium; confirming your suspicions about Set and Thor. However, you also found something which terrified you: the \cWarden{} and \cCaretaker{} have found unexpected traces of Kisrin in complex. That can only mean they're on your trail. Some of your Undoth technology gives off traces of Kisrin, and you don't know of anything else in the complex which would. This almost makes you happy that your WIDGET was stolen. Apparently \cAmaterasu{} has warned the AI that she has sensed a ``dark spirit'' in the complex, but they haven't taken her seriously or connected it to the Kisrin.

You also downloaded details of the complex's security systems. The autoheal system estimates four hours to bring everything back online. In order to escape successfully, the complex's teleportation grid will have to be disabled permanently. Otherwise, the \cWarden{} will just teleport you right back to your prison.

The complex also includes a ``Molecular Reassembler'' which can modify the nature of a wide range of intelligent lifeforms, making them stronger, weaker, or even killing them outright. Fascinating.


% The teleporter or something will not come back online for four hours.
% You must gain control of the security grid in order to escape.
% NOTE: You know you have four hours to escape (told by Warden or Caretaker?)

% Gain control of the security grid? Trying to get access to the teleportation grid? (Unity's method of escape.) Thinks now is a good time, because Unity's arrival is causing chaos. Maybe got an important bit of information even though he couldn't access the grid: The AI are on to him (Kisrin).
% Amaterasu is worrying him for some other reason.
%(learned that the AI lost contact with the Guardians).

% Learned about the Kisrin: must have been from the stolen device.

% And for several thousand years they didn't figure you out.
% You think Amaterasu is on to you.

Your time is running out before the Guardians figure out what you really are. You must find a way to escape back to Earth.


% \TODO{Could escape with Egypt, or Unity. Could even knock out Unity and take over his means of escape. But Unity is a pain, and has his own ideas for the humans. The Egyptians are fine.}

\begin{itemz}[Goals]
  \item Construct a radio and broadcast a signal to let other Undoth know where you are.
  \item Find a way to escape the Complex and return to Earth.
  \item Help your fellow Norse gods open the Bifrost bridge to Jotunheim so they're out of your way.
  \item Don't allow the Kisrin or any Undoth technology to be traced back to you.
  \item Don't allow \cAmaterasu{} to uncover your real identity.
\end{itemz}

\begin{contacts}
  \contact{\cOdin{}} The All-Father, ruler of the Norse gods.
  \contact{\cHel{}} The Norse goddess of the underworld.
  \contact{\cVal{}} A Valkyrie.
  \contact{\cAnubis{}} An Egyptian god of the underworld who is sympathetic towards you.
  \contact{\cAthena{}} A Greek goddess who wants to build an interstellar communicator. She has accepted the fact that she is a Celestial.
  \contact{\cAmaterasu{}} The only remaining Shinto goddess. She's trying to figure out which Celestial is not a Celestial.
  \contact{The \cCaretaker{}} One of the AIs who is imprisoning you here.
  \contact{The \cWarden{}} The other AI who is imprisoning you here.
  \contact{\cJascha{}} The senile Guardian who wanders around the Complex, pretending to be human.
\end{contacts}

\end{document}
