\documentclass[char]{guardians}
\begin{document}

\name{\cIsis{}}

% NOTE: There should be some preparation for escaping which is shared
% between the two methods of escaping.

% NOTE: If Osiris gets his powers back, he can protect them from Set?

% TODO: Set was not actually trying to escape. What help can he provide?
% Increase the number of people who escape with Unity?
% Substitute the Egyptians for other people escaping with Unity?
% What if Osiris and Set both help?
% TODO: Set will not be yearning for the stars.
% TODO: Two ways to resurrect; necronomicon and pandora's box.

It has been millenia since you last saw Egypt. Not this pitiful replica, but the real Egypt, where you could walk for days and days and still never reach the end. In this Complex, you can go from one end to the other in less than an hour.

You were brought here for reasons you have never learned by beings who call themselves the \cCaretaker{} and the \cWarden{}. These beings call you ``celestials'' instead of gods, and they're imprisioning you, many other gods, and even a few mortals. Some time after bringing you here, your jailers decided to hold a competition every hundred years. These Games brought you into contact with the gods of the other pantheons: Norse, Greek, and Shinto. These gods are strange and foreign to you. You enjoy the company of some of them, such as the Norse goddess \cHel{}. Others, like \cHera{}, you can't stand. She acts like you're encroaching on her role as goddess of marriage. Personally, you don't think she deserves that aspect, unless she's just claiming to be the goddess of wives who nag their cheating husbands.

\TODO{Give Isis more of a warning about Hera?}
% You're not sure she's entirely sane when it comes to other women.

After a millenium, some of the gods imprisoned here became so homesick it started to affect their sanity. Horus was among the first of the Egyptian gods to suffer this. Oddly, he didn't appear to long for Egypt, but instead for some strange place among the stars which was certainly nowhere he had ever been before. You suspected it was the influence of this strange Complex you've all been trapped in for so long. Horus, and everyone else who suffered this way, were taken away by the \cCaretaker{} and \cWarden{}. You could do nothing to stop them.

Over the centuries, more and more of your brothers and sisters were taken away, until only you, \cOsiris{}, \cAnubis{}, \cSet{}, and the mortal \cEgyptianHuman{} remained. Then, five centuries ago, \cSet{} also began to long for the stars. However, he died before the \cWarden{} and \cCaretaker{} could take him away. The cause of his death was an explosion that rocked the entire Complex and clearly worried even the \cWarden{} and \cCaretaker{}. You never found out what the cause of the explosion was, but you would not be surprised to find out that \cOsiris{} had something to do with it. \cAnubis{} suspected that \cSet{} was trying to circumvent your overseers' spells of protection in a desperate attempt to get out of the Complex, and unintentionally caused the explosion.

Eventually the three of you gods who remained, along with \cEgyptianHuman{}, decided to escape the Complex. Although the \cWarden{} and \cCaretaker{} have powers far beyond yours, they are not omnipotent, as they were clearly unsettled by the explosion which killed \cSet{}. You decided you could trust the Norse goddess \cHel{} enough to include her in your plans to escape. Since then you have discussed your plans using coded messages passed between pantheons by \cJascha{}, a mortal who your overseers have seen fit to allow free travel between all your realms. You've discussed many ideas, but only one has a real chance of working. If you can resurrect \cSet{} using the \iNecro{\MYname}, he may have knowledge of how to get past the security systems of the \cWarden{} and \cCaretaker{}. At the very least, having an ally your overseers don't know about is certain to help. \cOsiris{} has strong objections to this plan. You understand his loathing for \cSet{}, but escaping the Complex is too important to let that get in the way.

% \TODO{Revise the previous paragraph depending on how Set can actually help.}

At the last Games, seventy years ago, \cOsiris{}'s powers were stolen. Only he, you, and \cAnubis{} know of this. None of know has any idea who would have stolen them or why, but \cOsiris{} can tell they're still in the Complex somewhere. This is unsettling, and you would like to have the time to restore \cOsiris{}'s powers before you escape. But in the past two days events have happened which have accelerated your plans for escape.

A new god named \cUnity{} was brought to the Complex, for the first time in millenia. The \cWarden{} and \cCaretaker{} announced the Games were going to be held immediately because of \cUnity{}'s arrival, and \cOsiris{} immediately gave them the \iNecro{\MYname} as your pantheon's wager in order to delay any attempt to resurrect \cSet{}. You're beginning to be fed up with his resistance to your escape plan. At any rate, you'll need to win back the \iNecro{\MYname} in the Games (without letting \cOsiris{} hide it again), or maybe you can find another way to resurrect \cSet{} without it.

Yesterday, you saw signs that the power of the \cWarden{} and the \cCaretaker{} has weakened, at least temporarily. For a few moments, parts of Egypt flickered in and out of existence, and then all was back to normal---except that \cEgyptianHuman{} was killed by a falling pillar. \cEgyptianHuman{}'s death broke your heart. You have now failed every single one of your followers. Neither of the others seems to care: \cOsiris{} is only angry that there is nobody to worship him, and \cAnubis{} just embalmed \cEgyptianHuman{}'s heart in preparation for judgement. You begged \cAnubis{} to have mercy and refrain from judging him. \cEgyptianHuman{} was like a son to you, and you couldn't bear it if he was judged to be unjust. At least \cAnubis{} doesn't have the scales used to weigh the heart against the \iFeather{\MYname}\ldots{}

It's long past time you got out of this horrible place.

\begin{itemz}[Goals]
  \item Regain the \iNecro{} for your pantheon.
  \item Resurrect \cSet{}, either using the \iNecro{\MYname} or some other method.
  \item With \cSet{}'s help, escape the Complex with your pantheon and \cHel{}---even if it means knocking \cOsiris{} unconscious and dragging him with you over his objections.
  \item Don't allow \cAnubis{} to weigh \cEgyptianHuman{}'s heart against the \iFeather{\MYname}.
  \item Find out what caused the event that killed \cEgyptianHuman{}.
\end{itemz}

\begin{contacts}
  \contact{\cOsiris{}} Your husband. You love him dearly, but the issue of \cSet{} is beginning to drive a wedge between you.
  \contact{\cAnubis{}} The god of the afterlife, who judges the dead.
  \contact{\cHel{}} The Norse goddess who is in on your plans to escape.
  \contact{\cHera{}} The Greek goddess you can't stand.
  \contact{The \cCaretaker{}} One of the beings who is imprisoning you here.
  \contact{The \cWarden{}} The other being who is imprisoning you here.
\end{contacts}

\end{document}
