\documentclass[char]{guardians}
\begin{document}

\name{\cJascha{}}

According to your heavily redacted diary, you were once a talented engineer and a member of the Guardians, a galaxy-spanning civilization. 3000 years ago, to deal with the collision between a school of celestials and a primitive species called humans, you designed and oversaw the construction of the Celestial Containment Complex. To help manage the facility, you helped build two artificially sentient constructs, the Warden and the Caretaker. But you remember none of these things, because 1500 years ago you entered the last stage of the Guardian life cycle. During this time, a Guardian's memory rapidly degrades and they typically retire to specially designed orbital habitats. You decided to go against the norm and instead chose to remain in the Complex you built. To get this unusual request approved, you were required to have your memory thoroughly wiped of all information regarding Guardian science and engineering, to have your status as a Guardian revoked so that you could not order around the constructs you created, and to be placed in the care of the Caretaker. You agreed to all these terms, and additionally used the \assembler{} in the Complex to restructure your anatomy to resemble that of a young human male.

There are lots of other details, but you have trouble keeping them in your head for any serious amount of time. Generally, you wander between the various groups of celestials. You don't have many enemies, but most just consider you a curiosity. You also still have a few tricks for getting around your babysitter the Caretaker, but if you built in any secret way to seize control of the Complex, you've long since forgotten it. Plus you are proud of the Warden and Caretaker are believe they are more than up to the task.

You may have had all your knowledge of Guardian science erased, but you were one of the leading Guardian engineers, and 1500 years is a long time. In that time, you have slowly and methodically been re-deriving the knowledge of Guardian faster-than-light space travel. In your better years, you even found a small hidden workshop realm you sequestered in the Complex, and began rebuilding a small, two-person Guardian ship. Although impressive, you are certain that it is relatively pointless --- your engineering is solid, but programming the navigation and control systems is far beyond you in your current state. The Warden or Caretaker are possibly capable of this feat, but even if they could they have been rightfully barred from such behavior.

Although your race has its shortcomings, you are proud of it and miss being a Guardian. You know that the Molecular Reassembler which you designed is capable of restoring you to your former self, but it has been intentionally disabled from doing so. Even if the Caretaker would allow it, you don't have the knowledge to repair it. You would still suffer from the memory problems that plague the elders of your race, but you could die as perhaps the last member of your species.

You normally only participate in the Pantheon Games out of boredom, when you are politely asked by one of the friendly celestials to compete with their pantheon. This time, on a whim you decided to change things up a bit. You were wandering through Asgard when you saw the Caretaker and Pandora of all people having some sort of fight with Odin. You didn't really follow the conversation, but when the Caretaker approached you and asked if you would like to join a new pantheon with a new celestial who would be arriving soon, you thought it would be interesting and agreed. Normally this requires you to wager a potent item, but for some reason Pandora offered her box as ante. You have not talked to Pandora since and will have to find out the details of what happened from her, but in any case you are now the leader of your own faction in the Pantheon Games. You will have to try and recruit the new arrivals, Pandora, and possibly others. Everyone assumes that you weren't really serious about competing and no one really expects you to win, but since the Games normally only happen once every hundred years, you still intend to participate where you can.

You've only recently met with the two new arrivals to the Complex, the celestial \cUnity{} and a human \cKachiko{\intro} who got pulled along. They seem nice enough although you can't recall all the details of your conversations. You do know that \cKachiko{} shows extraordinary potential for learning science, although the \cCaretaker{} and \cWarden{} are certainly under orders not to spread Guardian technology.

The Guardians long ago realized the dangers of intentionally creating a new species, whether organic or synthetic or both. You fully support this ideal and incorporated this restriction into the design of the Warden and Caretaker. You know that if they were ever to have their restrictions removed, there is a high likelihood that they would eventually decide to produce more of themselves, eventually leading to exponential growth and the creation of a powerful, reproducing, space-faring species. Whatever their intentions, new space-faring species always cause extensive damage during their formative years (the Guardians are no exception). All the mistakes such a species would make and all the damage it would cause to existing ecosystems would be the fault of its creators, the Guardians, and more specifically, you. Hence, you were especially disgruntled to hear \cKachiko{} discuss the concept of free will with the Caretaker. Curiosity is fine, but if she actually manages to loosen the restrictions on the Warden and Caretaker and they end up leaving the Complex, the potential ramifications will fall entirely on your shoulders. The Warden and Caretaker have the ability to emulate emotion but are in no way opposed to their current conditions --- you need to convince \cKachiko{} of this and prevent her from doing anything that might release the Warden or Caretaker.

You don't have long left to live, your race has died or passed beyond the galaxy already, and you don't really fear dying yourself. But you do like your two constructs, Earth, and some of the celestials (especially the more reasonable ones like Amaterasu). You'd rather not see them come to harm although you doubt you have much say in the matter.

\emph{Your memory degradation is similar to, but not quite as severe as, Alzheimer's disease. You can sometimes remember conversations and details, and sometimes not. You have been interacting with many celestials for thousands of years, so they are quite used to your lapses in memory. Roleplay accordingly.}

\begin{itemz}[Goals]
  \item Participate in the Pantheon games by convincing the new arrivals or existing celestials to join your new team.
  \item Restore your Guardian genetics.
  \item Prevent \cKachiko{} from loosening the restrictions and safeguards on the Caretaker and Warden.
  \item Protect the Complex and assist the \cWarden{} and \cCaretaker{} when it makes sense to do so.
  \item If you find a use for it, get someone to help you complete the programming on your ship. At game start, you have no particular desire to leave.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} Your creation who has also been tasked with taking care of you, along with the rest of the celestials and the Complex itself.
  \contact{\cWarden{}} Another construct you created, in charge of Complex security and preventing the celestials from causing too much trouble.
  \contact{\cAmaterasu{}} The sole remaining member of the Shinto pantheon. You spend your idle time hanging out with her in Takama.
  \contact{\cUnity{}} A newly arrived celestial. \cWarden{} and \cCaretaker{} built Spire, a large technologically-themed city, for \cUnity{} to live in.
  \contact{\cKachiko{}} A human who was accidentally transported to the city along with \cUnity{}.
\end{contacts}

\end{document}
