\documentclass[char]{guardians}
\begin{document}

\name{\cKachiko{}}

My name is \cKachiko{\intro}. I come from a middle-class Japanese family, have a degree from the top robotics program in the United States, and after graduating I returned to Tokyo to found Kachicorp which I built from the ground up into a small but rapidly rising robotics company. I have a personal hand in every product my company makes and I work constantly to fundamentally changing the way we interact with robots in our daily lives. This is how my morning schedule was supposed to go: 9:00am, coffee with my secretary to go over the company finance report; 9:30am preparation for the 10:00am meeting with the marketing team regarding the upcoming convention in Yokohama; lunch at noon; 1:00pm working in the lab with my engineering team. This is, not, in fact, how my day has gone. I am not certain I will be home in time to take the roast out of the oven for dinner. I may or may not be alive by then.

At the end of my marketing meeting, a new event showed up on my schedule. Apparently my CTO had recently vetted an exceptionally talented new hire and that based on his excited tone it was absolutely imperative that I meet with the candidate in person if we were going to have a chance of hiring \cUnity{\them}. I made a mental note to remind my employees that we are a growing company and they will need to give me more than a few hours notice when these sorts of situations arise, but decided to just meet with the candidate over my lunch break. From the moment the candidate entered my office, I knew that \cUnity{\they} was like no one I had ever met before. \cUnity{\They} introduced himself as \cUnity{\intro}, and immediately jumped into a discussion so entrenched in technical detail that it was all I could do to keep up. \cUnity{} seemed to have an encyclopedic knowledge of my entire line of robots and had a seemingly endless stream of insightful suggestions to offer about each one, not to mention multiple entirely new designs. We had only just started delving into the details when I heard a deafening crack and a shimmering vortex began forming in the middle of my office. For those of you who have never witnessed a vortex appearing out of thin air, rest assured that it is quite an experience and leaves very little time to do anything besides stare blankly in disbelief and shock. Still, once the vortex began greedily absorbing the objects on my desk and started encompassing my desk itself, I rapidly transitioned from shock to flight, to no avail. \cUnity{}, on the other hand, hardly seemed surprised by the vortex's appearance and was studying it with only mildly concern. As I was pulled into the vortex \cUnity{\they} stood back watching me with passive interest, although I can only infer that as the vortex grew \cUnity{\they} was eventually pulled in as well.

When I came to I was in a city lifted directly from a science fiction movie. It was also evident that the entire city was under intense construction, although using tools and devices I have never seen before. Nearby, \cUnity{} was having an animated discussion with two other strange humanoid entities. Upon seeing me awaken, one of the entities came over and introduced \cCaretaker{\themself} as the \cCaretaker{}. \cCaretaker{\They} welcomed me to the Celestial Containment Complex, and in flawless Japanese wished to express \cCaretaker{\their} most sincere apologies for the inconvenience of my arrival as I was accidentally pulled in along with \cCaretaker{\their} actual target, \cUnity{}. If \cCaretaker{\their} insane claims are to be believed, \cUnity{} is an entity known as a celestial. Such beings are powerful and extremely dangerous to humans, and a galaxy-spanning race called the Guardians constructed this Complex to contain and suppress any celestials that come into contact with Earth. Can I speak to one of these Guardians? We would love to let you speak to the Guardians. How regrettable that the Complex has lost all contact with the Guardian homeworld over a thousand years ago. But rest assured that the \cCaretaker{} and her partner the \cWarden{}, two artificially sentient constructs created by the Guardians to oversee the Complex, are more than capable of assuring my happiness and security during my stay here. Can I go home? Oh surely quite soon, but not immediately as the spatial tunneling system is currently recharging, but would I like some tea? Yes. Yes I would like some tea. (Actually, despite my considerable misgivings, it turns out the \cCaretaker{} knows how to make excellent tea.)

The \cCaretaker{} was not going to get away with claiming to be a fully artificial being without some extensive tests being done. But every test I could think of to administer, every question both technical and philosophical, \cCaretaker{\they} came up with an answer at least as good (and often much better than) what I would expect of an adult human. Naturally it's possible that the \cCaretaker{} is just an avatar for a biological mind living somewhere else, but if this really is a sentient artifical intelligence I'm not going to pass up the opportunity to reverse engineer it. But as soon as I started probing the \cCaretaker{} about how exactly \cCaretaker{\their} mind worked, \cCaretaker{\they} regretted to inform me that it is a core directive from the Guardians that \cCaretaker{\they} and the \cWarden{} not spread Guardian technology in any way. What exactly are your core directives? \cCaretaker{\They} has to see to the well-being of all celestials and humans within the Complex and maintain the Complex facilities. And \cCaretaker{\they} must prevent any celestials or celestial-modified humans from escaping the Complex. And a long litany of other such  directives. Are you given any leeway in terms of these directives? What if they conflict? No, she only takes actions as dictated by her directives, and conflicting directives would be most regrettable. This lack of free will is quite bothersome. I may not understand the technology behind their AI brains, but I'm confident that all sufficiently intelligent life has the seed of self-worth that can reject such absolute restrictions. It may take a while, but I will not let the opportunity to learn the secrets of artificial sentience pass me by.

Despite the lack of any real progress or insights, I found that discussing the nature of intelligence with the \cCaretaker{} was a good way to take my mind away from my current predicament. In the distance \cUnity{} was engaging in a heated discussion with the \cWarden{}; \cUnity{} was not taking his captivity well at all and while \cUnity{\they}'s clearly responsible for me being here, if I'm going to have any hope of getting out of this madhouse I'll need \cUnity{\their} help. At some point the \cCaretaker{} left to go tend to something else and left me with a pad containing a brief summary of the Complex. Supposedly, the Complex was constructed 3000 years ago to contain a large school of celestials that had taken residence on Earth. These celestials still remain under the delusion that they are deities, and to keep peace among the celestials the \cCaretaker{} and \cWarden{} used a powerful artifact called the \stone{} to divide the Complex into realms modeled closely after each pantheon. The Greek pantheon lives in Olympus led by Zeus, the Norse pantheon lives in Asgard led by Odin, the Egyptians live in a partial reproduction of Egypt, and the Shinto celestials live in Takama. Turns out at some point the celestials revert to a disembodied interstellar form and the pantheons are much smaller now than they were in the past. The city I'm currently in, called Spire, was constructed using the \stone{} to be a home for \cUnity{} analogous to Asgard or Olympus.

At some point the \cWarden{} came over and without warning pricked me with a short needle. \cWarden{\They} claimed this would key me to the security fields of the Complex and was necessary for my own protection. \cWarden{\They} also gave me a long lecture about security within the Complex, not to trust the celestials, report any unusual activity or behavior to \cWarden{\them}, and so on. Exactly what I would expect of a security drone, and I have a feeling \cWarden{\they}'ll be even less forthcoming about any interesting technical details. A few minutes after the \cWarden{} left, \cUnity{} began taking apart one of the many computer terminals densely scattered throughout Spire, and while I was pondering what to do a strange man appeared around a corner and came up behind me. With an absent-minded expression he introduced himself as \cJascha{\intro}. He expressed his condolences that the \cCaretaker{} and \cWarden{} were not more forthcoming, but generally I had trouble sustaining a conversation with him. My pad doesn't mention \cJascha{} and I don't believe he is a celestial; I'm still not certain what to make of my interaction with him. After he left, \cUnity{} warned me that as far as he can tell the bubble surrounding the Complex was punctured to transport us here, but it will reseal itself in a matter of hours. Seeing as we're supposedly 10 miles beneath the surface of the moon, if we plan to escape we had better not still be here when it does.

While Spire is interesting, except for \cUnity{} it was also empty and I decided to wander outside the city to meet these entities impersonating humanity's pantheons. In what my pad told me was the central courtyard of the Complex, a group of extremely tall and fit people were engaging in intense banter. Apparently they were making preparations for the Games, a fairly ruthless exercise they perform every 100 years to prove which pantheon is the strongest. While observing from afar, a celestial who could only be \cAmaterasu{} came up to me. Although I'm not religious and I'm acutely aware that this is almost certainly not the \cAmaterasu{} of legend, as I talked with her I couldn't help but feel that she possessed more than a hint of divinity. Her Japanese accent was mesmerizing, and she seemed to grasp the nature of my plight almost instantly. She warned me that the other celestials were both powerful and capricious, and that as the goddess of both the sun and the universe, she seemed to agree with the \cWarden{} and considers it her duty to remain here and prevent the more dangerous celestial from escaping or otherwise allowing harm to come to Earth. Furthermore, she is certain that there is a dark spirit loose in the Complex and that it is somehow masking its presence from the \cWarden{}. \cAmaterasu{} feels that this spirit will take advantage of the disruption caused by \cUnity{}'s arrival to make its move. While I feel at peace around \cAmaterasu{}, I don't quite share her higher perspective. Preventing harm to Earth is all well and good, if I can manage it, but I'm more worried about myself.
                                                                                    
I'm not quite certain what to do now. My only ``friends'' here are \cUnity{} and \cAmaterasu{}. \cUnity{} is busying \cUnity{\themself} with Spire and I wouldn't be surprised if \cUnity{\they} was responsible for the skylight in the courtyard flickering out just now. But I can't deny \cUnity{\their} brilliance and I suspect he wants to know about Guardian science as much as I do. I'm confident that the \cWarden{} or \cCaretaker{} can be brought around to my side, if I can just find a way to weaken the strict constraints imposed on them by their creators. But mostly, I think I'm going to be busy over the next few hours avoiding getting squished by the deranged manifestations of Zeus, Odin, Anubis, and the like.

\begin{itemz}[Goals]
  \item Get out of here. Unless circumstances change and I decide I'd rather stay here.
  \item Explore the concept of free will with the \cWarden{} and \cCaretaker{} to help free them from some of the strict constraints imposed by the Guardians.
  \item Convince the \cWarden{} or \cCaretaker{} or someone else to give me more details on how to create artificial sentience.
  \item Learn whatever else I can about Guardian technology. If I leave, I want to take any and all technology I can with me. Who knows, I may even be able to convince the \cWarden{} and \cCaretaker{} to come back with me. If I can't escape, I at least want to find a way to transmit what I've found back to Earth.
  \item Find out more about what is going on here and the history of the Complex. If I make it out I doubt I'm coming back.
\end{itemz}


\begin{contacts}
  \contact{\cUnity{}} The being the \cWarden{} and \cCaretaker{} were aiming to capture, which dragged me into this mess in the first place.
  \contact{The \cCaretaker{}} A sentient being created by the Guardians who claims to be in charge of taking care of the facilities and the celestials.
  \contact{The \cWarden{}} The counterpart to the \cCaretaker{}, in charge of security and preventing celestial escape.
  \contact{\cAmaterasu{}} The Shinto goddess of the sun and universe.
  \contact{\cJascha{\intro}} A human who seems to have free reign of the Complex.
\end{contacts}

\end{document}
