\documentclass[char]{guardians}
\begin{document}
\name{\cPandora{}}

You are a construct of \cZeus{}, \cAthena{}, and \cHephaestus{}. You were created in order to protect your box.  \cZeus{} in \cZeus{\their} infinite wisdom saw fit to create a container for \emph{something}, and charge you with protecting it. What an exciting life. \#sarcasm.

You were swept up with the Greek Pantheon by the \cWarden{} and \cWarden{\their} associate, the \cCaretaker{} a couple of thousand years ago. Something about beeing too contaminated bo the Gods to be allowed to remain on earth. Of course you were ``contaminated'', you were a \emph{construct}. A human, even one protected by \cZeus{}, among Gods should have been killed intentionally or accidentally within a days. The \cWarden{} had other plans however. By taking some of your blood upon arrival, the \cWarden{} gave you \cWarden{\their} own protection. The very air around you absorbs attacks and prevents you from taking any damage.

The \cCaretaker{} was \emph{very} concerned with the wellbeing of the Gods, and came up with all kinds of stupid ideas, including building separate homes for the Greek, Norse, Egyptian and Shinto pantheons. \cCaretaker{\They} and the \cWarden{} used the \stone{} to create a copy of Mt. Olympus. \cZeus{} quickly decided that he wanted the stone for \cZeus{\them}self, and you resigned yourself to helping rather than risk \cZeus{\their} wrath.

The \cCaretaker{} also invented the \pGames{} to try to entertain the Gods. It was a welcome diversion for them, although you hated being forced to participate. You were never good enough to stack up to the Gods. Whichever competition you competed in, the Greeks would lose. At best this brought ridicule down on your head.

For the next 2000 years, your life was a living hell. The Gods were like petulant children and tormented you constantly -- and all of them save the three who created you, and your adoptive mother \cHera{}. They couldn't kill you, but they could do everything from trip you, to spirit you hundreds of feet into the air just to watch you fall.  They pulled your hair, called you names, and worst of all, would take your box and threaten to open it.  Even though they had all been forbidden by \cZeus{} to do so, they loved to see your panicked reaction when they took the box. You became even more fiercely protective of your box, and avoided the company of everyone. 

You don't know what is in the box, honestly you don't much care. What matters is that \cZeus{} trusted \emph{you} with it, and not one of his actual children. \cZeus{\They} \emph{created} you for this purpose. In fact, it was the only purpose you had. If you failed it, what value would you have? That thought drove you for a long time, and embittered you toward the Gods who wished to take it away from you. The box -- and therefore \cZeus{}'s trust -- is all you had.

One by one, the Gods started to disappear. There was always a big party, which you of course avoided, and a ship. If only that ship could carry \emph{you} away instead. How you longed to leave the confines of the Complex. You watched earth through the viewing screens with a hunger to rival the God's desire for the stars. It all seemed so hopeless though.  The \cWarden{} and \cCaretaker{} had managed to imprison the Greek Gods, and you, as a mere construct, could not even deal with the gods. How could you possibly compete with their captors?

You sunk into a deep depression, that nobody noticed except \cHera{}. To your great surprise, \cHera{\they} showed genuine concern for you. Perhaps \cHera{\them} dominion over mothers and wives was not as misplaced as you originally thought. Over the years, the two of you became close, especially as \cHera{} and \cAthena{} grew apart -- they were constantly fighting.

About 500 years ago, there was an incident that really rocked the complex -- literally. Normally when Gods started whining about the stars, the \cWarden{} and \cCaretaker{} would throw a big celebration and all, but when \cSet{} and Thor decided they were bored of this prison and wanted to leave, there was no such celebration. Things grew tenser and tenser as the two Gods became more and more restless. They started acting out, and you waited with bated breath to see how the \cWarden{} would punish them. So many long years here and you may have absorbed some of the sadistic tendencies of the Gods.  Rather than some big, dramatic confrontation though, there was something far more mysterious. One night, there was a huge explosion that shook the complex, and the next morning both \cSet{} and Thor were gone. All of the gods were in tizzy over it, and no one could speak of anything else during the next games. You simply counted two fewer who would torment you.

About 100 years ago, you found an unexpected ally. The \cWarden{} approached you late one night with a proposition. He could sense your dislike of the gods (Somebody get \cWarden{\them} them the Understatement of the Year Award.) Regardless, \cWarden{\They} offered you a deal. The \cWarden{} claimed to have the power to send you back to earth. Of course \cWarden{\they} wanted something first. \cWarden{} offered you a gun -- supposedly with the ability to take away a God's power.  All you had to do was take away all of the Gods' powers. \cWarden{\They} was suspiciously vague about why \cWarden{\they} was offering this to you, rather than just doing it \cWarden{\them}self. The \cWarden{}'s opinion of the gods was no secret. And yet, how could you pass up such a chance to get even with the gods? You took the gun. The \cWarden{} cautioned you that the gun would take some time to recharge between uses, and that you must be careful not to get caught by the \cCaretaker{}. Apparently the \cWarden{} was doing this without \cCaretaker{\them} blessing. Interesting\ldots{}

Rather than try the gun on the Greek Pantheon first, since it had dwindled to \cZeus{}, \cAthena{}, \cHephaestus{}, and \cHera{}, the four Gods who had ever shown you kindness and some semblance of respect, you decided to wait for a chance to attack one of the other Pantheons.  During the \pGames{} 70 years ago, you took your chance. Just as the games were concluding, you snuck back to your chambers and grabbed the gun. You pointed it at \cOsiris{} and pulled the trigger. The gun shook in your hands, and for a moment you feared that it might explode, but then a beautiful ball of red light formed inside the storage container of the gun. You quickly whisked it off and sealed the jar as the \cWarden{} had shown you.

You grinned gleefully as the \cCaretaker{} announced the end of ``Team Building'' time and insisted that each pantheon return to it's seperate confinement. You had done it! You had successfully stolen a God's power. Then reality washed over you. What were you supposed to do with it? Would the other Gods recognize the glowing orb as a God's power? You debated your options and concluded that \cHephaestus{} was your best option. \cHephaestus{\They} was treated almost as badly as you by the other gods, and would likely jump at the chance to get back at them too. You therefore approached \cHephaestus{} in \cHephaestus{\their} forge.

\cHephaestus{} asked fewer questions than you were afraid \cHephaestus{} might. \cHephaestus{} wanted only to know if \cHephaestus{\they} could keep the orb. You didn't care, in fact it was probably better this way -- \cHephaestus{} might forget who gave it to \cHephaestus{} and wouldn't that be convenient? Unfortunately, the mechanical golem that \cHephaestus{} put the orb of \cOsiris{}'s power into jumped smartly to life. \cHephaestus{} was so happy with the results that \cHephaestus{\they} wanted to know if you could acquire more of these orbs. You were rather evasive about this, but said that you'd see what you could do. You savored the power reversal -- a God needed something from you! For the next 70 years, your biggest concern was that \cHephaestus{} would ask you about more orbs in front of the other Greeks.

A few hours ago, your mostly boring, occasionally rotten existence was turned on it's head. A new god named \cUnity{} arrived at the complex, the \cCaretaker{} decided to host \pGames{} early, to welcome \cUnity{\them}. With that announcement, the greek pantheon was thrown into a flurry of activity. \cZeus{} and \cHephaestus{} declared their plan to build new Mt. Olympus to be ready to implement. There were of course a few last minute things that had to be arranged. Most of them didn't concern you. \cZeus{} declared you in charge of a critical part of the mission. You beamed with pride at being chosen -- until you heard what you were being asked to do. It was your task to sneak into the Norse pantheon's home realm and steal \iHammer{}. It seemed impossible to do, but when \cZeus{} said ``jump'' you didn't even bother asking how high.

Off you went to Asgard. You got fairly close too. You managed to get as far as the armory before you were found. \cHel{} found you, and \cHel{\they} was understandably furious. You didn't even bother to stifle a yawn as \cHel{\they} ranted at you though, since it's not like \cHel{\they} could do anything to you.

\begin{itemz}[Notes]
  \item\textbf{Psychlim:} ``My Box'' You are almost constantly thinking about your box. You carry it everywhere for fear that someone might take it when you aren't looking. You are not willing to be parted from your box for more than a few seconds. You will actively try to prevent anyone from taking the box, or, Gods forbid, opening it. Feel free to role play your obsession appropriately.
\end{itemz}

\begin{itemz}[Goals]
  \item Find a way to escape the Complex with \cUnity{} or \cOdin{}, or otherwise.
  \item Figure out if you should open your box or not. Regardless, don't ever let it out of your sight.
  \item Help the Greek Gods win the \pGames{}. If they lose and you fail to escape, the next 100 years will be unbearable.
  \item Steal the powers of as many gods as possible.
\end{itemz}


\begin{contacts}
  \contact{\cZeus{}} Your \cZeus{\parent} and the leader of the Greek Pantheon.
  \contact{\cHera{}} Your \cHera{\parent}, the two of you have grown close over the years.
  \contact{\cAthena{}} Your \cAthena{\sibling}, you barely exist as far as \cAthena{\they} is concerned.
  \contact{\cHephaestus{}} Your \cHephaestus{\sibling}, you barely exist as far as \cHephaestus{\they} is concerned.
  \contact{\cWarden{}} The closest thing you have to a friend in this place of Gods.
  \contact{\cOdin{}} Leader of the Norse pantheon. He may help youa escape the Complex.
\end{contacts}

\end{document}
