\documentclass[char]{guardians}
\begin{document}

\name{\cUnity{}}

Two days ago, I was dead. Yesterday, I was \cUnity{\intro}, a god among mortals. Today, I'm in a prison inhabited by insane anachronisms and run by the malfunctioning constructs of an extinct species. I have every intention of getting out of this madhouse, but my window of opportunity to escape is frighteningly short. I barely know their names, but I'll have no choice but to try and work with these bizarre ``deities'' if I'm going to have any chance of breaking free.

My first moment of consciousness was confusing, to say the least. One moment I was a disembodied, unthinking speck, the next I was filled with the knowledge, ambition, thoughts, dreams, and troubles of a thousand humans. I knew how to prove the halting problem is undecidable, the various safety concerns that have to be taken into consideration when building a nuclear power plant, and the design schematics of the successor to the Tesla Model S.  My next few hours of existence were breathtaking. I had a perspective no human had ever possessed before, encompassing all of modern science, mathematics, and engineering, and I started connecting the dots. The breeder reactor design for thorium reactors can be optimized to surpass the efficiency of uranium fuel plants. I developed a lower-temperature synthesis pathway for sulfuric acid. And I came up with hundreds of experiments that I still intend to carry out on the drosophila melanogaster genome. While captivating, at some point I realized that these vast leaps of progress in modern science would go nowhere unless I started putting them into practice. So I decided it was time to look around and figure out who, what, and where I was.

I was pleasantly surprised to discover that I seemed to be inhabiting a human body with a perfectly functional set of limbs and senses. I even had clothes on, a marvelous development as there was honestly no time to waste on trying to purchase any. Taking stock of my surroundings, I deduced I was at the Akihabara district in Tokyo, certainly an acceptable location to start putting my plans into motion. Wandering into an electronics store, I gained access to the most marvelous collection of knowledge yet known, \emph{The Internet}. Realizing I could become lost on this network for years, I managed to summoned enough willpower to resist its call and focus my search on finding a suitable target for my plans. Weighing a number of factors, I eventually settled my sights on Kachicorp, a nearby robotics company  founded by \cKachiko{\intro}, a quite respectable roboticist. In the thirteen minutes it took me to navigate through the Tokyo Rail system to Kachicorp HQ, I had come up with three modifications to existing Kachicorp products and five new models. I estimated that within the week I would have displaced the existing CTO and laid the foundations for my plans to restructure the academic and industrial complexes of the world to suit my ever-growing plans for applied rationality, scientific progress, and eventual interstellar exploration and colonization. %Disappointingly, my timetable has been delayed by several hours by recent events but I have every intention of getting things back on track momentarily.

Upon arriving at Kachicorp, assisted by the woefully inadequate security on their internal calendar system, within thirty minutes I had arranged a meeting with the CEO, \cKachiko{}. Perhaps I should have found a more tactful way to approach the subject, as she seemed overly preoccupied with small details such as how I knew such intimate details of the schematics of Kachicorp. But once I got over these bumps and she realized the brilliance of my new designs, she lost herself in the potential of what I was describing. I found the resonance between myself and Kachiko intoxicating --- nothing is more rewarding than working with like-minded individuals to further our ambitions.

This is around the time things started to go wrong. While I was showing \cKachiko{} my design for a semi-automatic cooking system, a shimmering white vortex appeared in the room. Although I had no rational explanation for this phenomenon, I wasn't overly surprised; after all, my own existence seems to run quite contrary to the scientific consensus. Given that the vortex was rapidly sucking in all the objects in the room, I attempted to flee with no success. I waited until \cKachiko{} was pulled inside, hoping it might be sated upon acquiring a human consciousness, but as I expected the vortex was out for me alone and eventually I too was pulled through.

I awoke with \cKachiko{} in a city under construction. A strange humanoid entity walked up to us and introduced itself as the Caretaker. It claimed that I was an entity known as a Celestial and that I present an unacceptable danger to the human population on Earth. It was consequently necessary for the \cCaretaker{} and its companion the \cWarden{} to transport me to their facility, the Celestial Containment Complex. They were building this city, Spire, as a place for me to ``feel comfortable'' during my stay here. While its architecture is indeed impressive it was also painfully apparent that I will not be allowed to advance any of my agendas here.

Once given a chance, I called up the myriad of ``welcome'' documents the \cCaretaker{} was willing to provide. Apparently there are numerous other entities similar to myself trapped here, although they seem to be under the delusion that they represent deities from various time periods in human history. The largest pantheon seems to be Greek unsurprisingly led by Zeus, followed by Odin leading the Norse pantheon, an Egyptian pantheon with unclear leadership, and finally Amaterasu being the sole representative from the Shinto pantheon.

The Complex itself and both the \cCaretaker{} and \cWarden{} seem to be artifacts of a formerly galaxy-spanning race called the Guardians. In their vast wisdom they wandered the galaxy preventing \emph{dangerous beings} such as myself from interacting with innocent children such as humans, suppressing and killing evil species such as the \evilRace{}, and generally turning the entire galaxy into a micromanaged nanny-state. In their vast wisdom they also seem to have vanished 1000 years ago for unknown reasons, and the \cCaretaker{} and \cWarden{} are running off millennia-old instructions. Although they are amazing hard-AIs, they appear to possess no semblance of free will, exhibiting only absolute loyalty to the Guardians and their last commands to contain and care for all Celestials that attempt to interact with Earth. Although I loathe my containment, I also can't help but be excited by the fact that the Guardians are light-years ahead of human technology. I want to learn everything I can about their technology, but especially the secret of artificial sentience exemplified by your two jailers and the mechanisms that facilitate faster-than-light travel and communication.

\cKachiko{} was understandable shaken by this rather abrupt turn of events, but she seems to be adjusting well. Once she realized that your jailers were just 

\begin{itemz}[Goals]
  \item Freedom.
\end{itemz}


\begin{contacts}
  \contact{\cCaretaker{}} An ancient dragon who called this council meeting.
\end{contacts}

\end{document}
