\documentclass[green]{guardians}
\begin{document}
\name{\gOlympus{}}

This sheet explains how to build New Mt. Olympus. \cHephaestus{} has determined that if the endeavor is successful, New Mt. Olympus will exist in a pocket dimension, and be completely outside of the control of the \cCaretaker{} and \cWarden{}. It will lack contact with Earth, but \cZeus{} has decided that this is an acceptable trade off to escape the \cCaretaker{} and \cWarden{}.

Preparations for New Mt. Olympus have been underway for centuries, but \cUnity{}'s arrival has caused plans to be accelerated because it appears that it may now be possible to gain access to the \stone{}. The final steps to build New Mt. Olympus must be completed before the \cCaretaker{} and \cWarden{} regain complete control of the complex.

In order to build New Mt. Olympus, the following steps must be taken, \emph{in order}. Once completed, a doorway to the pocket dimension will open for \bf{30 minutes}.

\begin{enumerate}
  \item Get the aspect of \bf{Power} cast on someone. That person must then deck a hand of 4 or better to break the shield surrounding the \stone{}.
  \item Get the aspect of \bf{Eternity} or \bf{Trickery} cast on the stone itself.
  \item Get someone blessed with the aspect of \bf{Royalty}, and have then recite the following poem in the presence of 3 witnesses:\\ \\
Mount Olympus home to many Gods that ruled the Earth, \\
The highest mountain of Greece, that represented power and mirth, \\
Home of Zeus the youngest son of Cronus and Rhea, the King of Gods, \\
The all powerful ruler of the skies retaining power from the lightning rod, \\
Wedded to Hera the Queen of the Gods, Goddess of marriage and motherhood, \\
The Goddess of women over the world, to make women’s power understood, \\
Great Mount Olympus, home to Athena, Goddess of wisdom, strategy and war,\\
Sired by Zeus, patron of Athens, to the just a companion and counselor.\\
Where weapons and tools, in the hands of Hephaestus, take shape for use by the Gods.\\
Son of Hera the God of forging, fire and innovation, earns mortal laud \\
The proof of Gods on Mount Olympus their deeds spread the common belief. \\
 
\end{enumerate}

\end{document}
