\documentclass[green]{guardians}
\begin{document}
\name{\gReassembler{}}

The Molecular Reassembler is a device developed by the Guardians. It is a big container that can easily accommodate a large human body, and is designed to modify the molecular structure of whatever is placed within the vessel. The device is versatile, with the most readily available settings provided below.

Using the Molecular Reassembler requires the \aGuardianTech{} ability and one or more Aspects. To start the device, the recipient must be restrained in the chair. They do not have to be willing or conscious, and do not need to be told which setting you are using. Then you or someone else must invoke one of the listed Aspects on your behalf. You must spend at least one minute interacting with the device, which can be interrupted (this will not consume the Aspect). When you finish, tell the recipient to open the packet listed after each setting.

\remark{Some of these abilities may be moved into ability packets that are rewards for research notebooks. Just getting access to the reassembler is non-trivial except for the AIs.}

\subsection{Settings}

\begin{itemize}

\item \textbf{Enhance Genetic Structure; Aspect of Eternity, Power, or Motherhood; $\Gamma$ packet} --- Significantly enhances the genetics of a human, granting vastly improved health and longevity along with enhanced intelligence, agility, and strength. Has no effect on celestials.
\remark{Makes Kachiko and optionally Pandora or Jascha super-smart. Unity wants this for his followers. I suppose it could also be used on gods-turned-mortal. Certain mechanics (ex. escape) require a certain number of super-smart participants. Some gods may already be thusly augmented.}

\item \textbf{Human Reversion; Aspect of War, Mortality, or Justice; $\Gamma$ packet} --- Permanently and irrecoverably turns a celestial into a mortal human, eliminating all of their celestial abilities and immunities. Has no effect on non-celestials.
\remark{Pandora and the Warden want this for many gods. The warden could give them a forcefield if it wanted to, otherwise they have CR 1.}

\item \textbf{Demolecularization; Aspect of Death, Destruction, or Vengence; $\Omega$ packet} --- Breaks everything in the vessel down into its molecular components. The recipient should immediately go "NOT HERE", and find a GM, taking their items with them.
\remark{Only way to kill the AIs? All the items are destroyed.}

\item \textbf{Resurrection and Rebirth; Aspect of UNKNOWN; $\Omega$ packet} --- A deceased human corpse may be brought back to life, so long as they died within the past 30 minutes.
\remark{Caretaker only?}

\item \textbf{Celestial Suppression; Aspect of Protection, War, or Destruction; $\Gamma$ packet} --- Permanently and irrecoverably destroys key components of the celestial biological cycle. This will freeze a celestial in its current form, preventing further life stages from occurring. Guardian protocols specifically prohibit this type of intervention in the lifecycle of other species, considering it to be equivalent to murder or forced castration. Has no effect on non-celestials.
\remark{Not a default ability. One solution for the stage-three celestials.}

\item \textbf{Guardian Restoration; $\Omega$ packet} --- Re-establishes Guardian genetics in a former Guardian.
\remark{Not a default ability. Can restore Jascha, but with enough research also turn someone else into a Guardian for the purposes of the AIs. For a God, they might have to first go through being a human, which could be traumatic and involves trusting a third party.}
	
\end{itemize}

If you gain an ability starting with "Molecular Ressembler Setting", you may use that setting on the Molecular Ressembler so long as you still have the \aGuardianTech{} ability.

\end{document}
